### 2023-08-18 paper/paper.tex
Added paper skeleton

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[remotesensing,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{John Waczak $^{1,\dagger,\ddagger}$\orcidA{}, David Lary $^{2,\ddagger}$ and Firstname Lastname $^{2,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{John Waczak, David Lary and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Waczak, J.; Lary, D.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3.} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Recent developments in hyperspectral imaging technology have led to dramatic reductions in both size and weight of imaging platforms. Due to these improvements, it is now possible to incorporate the technology as the payload of autonomous aerial vehicles such as drones. However, the massive volume of hyperperspectral datacubes poses significant computational challenges to their adoption in real-time applications. In this paper, we develop a procedure for the rapid georectification of pushbroom imagery and demonstrate its application for real-time remote sensing... Results indicate that a typical image can be processed in ~10 seconds while it takes $x$ seconds to capture. }

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%

%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars. Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it. Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
%\textbf{What are the main findings?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}\vspace{3pt}
%\textbf{What is the implication of the main finding?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.

\section{Introduction}
Overview of Hyperspectral Imagery

Multi-spectral vs Hyperspectral imagery

Paragraph about previous uses of HSI technology in remote sensing applications. Plant health, NDVI, water applications, land management, etc...

Challenges of using HSI in real-time applications: Data volume, processing power, data streaming. Data are much to big to be streamed to the ground in real time; for this application, imagery need to be collected, georeferenced, and then turned into data products \emph{onboard the drone} before they can be readily streamed to the ground. We can always re-process the imagery later for an in-depth reanalysis, but for time-critical applications, we need all of the processing to happen on board the drone.

Application: Our robotic team

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
Overview of the HSI

Overview of the Aerial Vehicle Platform (w/ NUC and SSD)

Georectification Procedure.
\begin{itemize}
    \item collect datacube 
    \item read HSI in ENVI format
    \item read Flight Data 
    \item interpolate flight data to HSI times 
    \item read Downwelling irradiance spectrum
    \item convert radiance to reflectance 
    \item georectify to obtain new coordinates 
    \item resample to regular grid
    \item save results to HDF5
\end{itemize}

Code and data availability via OSN and Github

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\begin{list}
    \bullet Create table with processing timings for each step on a typical HSI
    \bullet Create second table comparing time for full processing including resampling to a variety of scales (e.g. 5 cm, 10 cm, 25 cm) We will want a version of the processing function that does not include the uncertainties and the spectral indices
    \bullet create additional table showing size of each of the data producs and their step in the pipeline (ending with a dataproduct like the NDVI)
    \bullet Create a figure showing the georeferenced image on top of the satellite background 
    \bullet Create another figure of the entire map with a spectral index applied to one of the dye-release datasets (to demonstrate use for real-time application like oil-spill)
    \bullet create a figure of a sample HSI datacube in 3-d like from the previous paper with the rgb image on the top. 
\end{list}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data \textsuperscript{1}\\
\bottomrule
\end{tabularx}
\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
			  	                   & Data			& Data			& Data\\
			             	      & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
			  	                  & Data			& Data			& Data\\
			             	     & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
                  \midrule
\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{* Tables may have a footer.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data. In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Where no new data were created, or where data is unavailable due to privacy or ethical re-strictions, a statement is still required. Suggested Data Availability Statements are available in section “MDPI Research Data Policies” at \url{https://www.mdpi.com/ethics}.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the~results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}
\end{document}

### 2023-08-19 1b_visualize-HSIs.jl
nearly have working code

@@ -14,7 +14,6 @@ println("Output dir: $outpath")
 
 
 
-
 # create a plot of the HSI path on a satellite background tile
 w= -97.717472
 n= 33.703572

### 2023-08-19 1c_timing-tests.jl

@@ -1,0 +1,50 @@
+using RobotTeam
+using HDF5
+using BenchmarkTools
+import CairoMakie as cmk
+using MintsMakieRecipes
+cmk.set_theme!(mints_theme)
+
+include("utils/vis_tools.jl")
+include("utils/config.jl")
+
+basepath
+
+files = get_raw_file_list.(get_bil_files(basepath, "Scotty_1"))
+
+f = files[1]
+
+hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
+
+
+xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ, Data_σ = resample_datacube(hsi; Δx=Δx)
+
+
+idxs = findall(IsInbounds)
+Data_μ[1,idxs[1]]
+eltype(Data_μ)
+
+
+
+
+t = @benchmark HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
+tune!(t)
+
+
+# make sure to run the timings for multiple values of Δx e.g.  0.05, 0.1, 0.25, 0.5
+
+# fib(n) = n <= 1 ?  1 : fib(n - 2) + fib(n - 1)
+# suite = BenchmarkGroup()
+# suite["fib"] = BenchmarkGroup(["tag1", "tag2"])
+# suite["fib"][10] = @benchmarkable fib(10)
+# suite["fib"][20] = @benchmarkable fib(20)
+
+# t = @benchmark fib(10)
+
+# tune!(suite)
+# results = run(suite, verbose = true)
+
+# BenchmarkTools.save("output.json", median(results))
+
+
+

### 2023-08-19 3__colocate.jl

@@ -4,8 +4,64 @@ using HDF5
 using Dates
 using CSV, DataFrames
 using HDF5
+using ProgressMeter
 
 include("utils/vis_tools.jl")
 include("utils/config.jl")
 
-test_path = "/media/jwaczak/LabData/RobotTeam/processed/hsi/11-23/Scotty_1/Scotty_1-1.h5"
+targetpath = "/media/jwaczak/LabData/RobotTeam/prepared/11-23/Targets.csv"
+basepath = "/media/jwaczak/LabData/RobotTeam/processed/hsi/11-23"
+@assert ispath(targetpath)
+@assert ispath(basepath)
+
+df_in = CSV.read(targetpath, DataFrame)
+gdf = groupby(df_in, :predye_postdye)
+
+
+df = gdf[(predye_postdye="Pre-Dye",)]
+
+
+names(df)
+
+# initialize array and set to NaNs
+X_features = Matrix{Float64}(undef, nrow(df), length(features_dict[:varnames]))
+X_features .= NaN
+
+
+function update_features!(X_features, df, collection_id)
+    for (root, dirs, files) ∈ walkdir(joinpath(basepath, collection_id))
+        for f ∈ files
+            if endswith(f, ".h5")
+                fpath = joinpath(root, f)
+                @info "Working on $(fpath)"
+                h5open(fpath, "r") do h5
+                    X_h5 = read(h5["data-Δx_0.1/X"])
+                    Y_h5 = read(h5["data-Δx_0.1/Y"])
+                    IsInbounds = read(h5["data-Δx_0.1/IsInbounds"])
+
+                    Xmin,Xmax = extrema(X_h5)
+                    Ymin,Ymax = extrema(Y_h5)
+
+                    Xs = [x for x ∈ X_h5, y ∈ Y_h5]
+                    Ys = [y for x ∈ X_h5, y ∈ Y_h5]
+
+                    @showprogress for i ∈ 1:nrow(df)
+                        row = @view df[i, :]
+                        if row.X ≥ Xmin && row.X ≤ Xmax && row.Y ≥ Ymin && row.Y ≤ Ymax
+                            idx = findfirst(row.X .== Xs .&& row.Y .== Ys)
+                            if IsInbounds[idx]
+                                X_features[i,:] .= h5["data-Δx_0.1/Data_μ"][:,idx]
+                            end
+                        end
+                    end
+                end
+            end
+        end
+    end
+end
+
+
+
+collection_id = "Scotty_2"
+
+update_features!(X_features, df, collection_id)

### 2023-08-19 utils/config.jl

@@ -1,6 +1,9 @@
+# basepath = "/media/jwaczak/Data/robotteam-data/raw"
 basepath = "/media/jwaczak/LabData/RobotTeam/raw/hsi"
 @assert ispath(basepath)
 
+
+# outpath = "/media/jwaczak/Data/robotteam-data/h5"
 outpath = "/media/jwaczak/LabData/RobotTeam/processed/hsi"
 if !ispath(outpath)
     mkpath(outpath)
@@ -60,3 +63,70 @@ n= 33.703572
 s= 33.700797
 e= -97.712413
 
+
+
+
+features_dict = Dict(
+    :varnames => [
+        ["R_"*lpad(idx, 3,"0") for idx ∈ 1:462]...,
+        "roll",
+        "pitch",
+        "heading",
+        "view_angle",
+        "solar_azimuth",
+        "solar_elevation",
+        "solar_zenith",
+        "mNDWI",
+        "NDVI",
+        "SR",
+        "EVI",
+        "AVRI",
+        "NDVI_705",
+        "MSR_705",
+        "MNDVI",
+        "VOG1",
+        "VOG2",
+        "VOG3",
+        "PRI",
+        "SIPI",
+        "PSRI",
+        "CRI1",
+        "CRI2",
+        "ARI1",
+        "ARI2",
+        "WBI",
+        "MCRI",
+        "TCARI",
+    ],
+    :printnames => [
+        ["Reflectance Band "*lpad(idx, 3,"0") for idx ∈ 1:462]...,
+        "Roll",
+        "Pitch",
+        "Heading",
+        "Viewing Angle",
+        "Solar Azimuth",
+        "Solar Elevation",
+        "Solar Zenith",
+        "Modified Normalized Difference Water Index",
+        "Normalized Difference Vegetative Index",
+        "Simple Ratio",
+        "Enhanced Vegetative Index",
+        "Atmospherically Resistant Vegetative Index",
+        "Red Edge Normalized Difference Vegetation Index",
+        "Modified Red Edge Simple Ratio",
+        "Modified Red Edge Normalized Vegetation Index",
+        "Vogelmann Red Edge Index",
+        "Vogelmann Red Edge Index 2",
+        "Vogelmann Red Edge Index 3",
+        "Photochemical Reflectance Index",
+        "Structure Intensive Pigment Index",
+        "Plant Senescence Reflectance Index",
+        "Carotenoid Reflectance Index",
+        "Carotenoid Reflectance Index 2",
[…]

### 2023-08-20 2__parse-boat-data.jl
finished up colocation script. Much faster when we don't chunk the hdf5 files

@@ -7,10 +7,10 @@ using HDF5
 include("utils/vis_tools.jl")
 include("utils/config.jl")
 
-boatpath = "/media/jwaczak/LabData/RobotTeam/raw/boat"
+boatpath = "/media/teamlary/LabData/RobotTeam/raw/boat"
 @assert ispath(boatpath)
 
-outpath = "/media/jwaczak/LabData/RobotTeam/processed/boat"
+outpath = "/media/teamlary/LabData/RobotTeam/processed/boat"
 if !ispath(outpath)
     mkpath(outpath)
 end
@@ -40,7 +40,7 @@ for (date, paths) ∈ paths_dict
 end
 
 
-prepared_path = "/media/jwaczak/LabData/RobotTeam/prepared"
+prepared_path = "/media/teamlary/LabData/RobotTeam/prepared"
 if !ispath(prepared_path)
     mkpath(prepared_path)
     for dts ∈ collection_dates
@@ -66,7 +66,7 @@ end
 
 
 # now we want to get the "category" for the flight so we can carefully sort by time.
-hsi_path = "/media/jwaczak/LabData/RobotTeam/raw/hsi"
+hsi_path = "/media/teamlary/LabData/RobotTeam/raw/hsi"
 @assert ispath(hsi_path)
 
 
@@ -156,4 +156,3 @@ for (day, categories) ∈ collection_times
 end
 
 
-# now let's go through each boat csv and add the category column

### 2023-08-20 3__colocate.jl

@@ -9,23 +9,13 @@ using ProgressMeter
 include("utils/vis_tools.jl")
 include("utils/config.jl")
 
-targetpath = "/media/jwaczak/LabData/RobotTeam/prepared/11-23/Targets.csv"
-basepath = "/media/jwaczak/LabData/RobotTeam/processed/hsi/11-23"
-@assert ispath(targetpath)
-@assert ispath(basepath)
-
-df_in = CSV.read(targetpath, DataFrame)
-gdf = groupby(df_in, :predye_postdye)
-
-
-df = gdf[(predye_postdye="Pre-Dye",)]
-
-
-names(df)
-
-# initialize array and set to NaNs
-X_features = Matrix{Float64}(undef, nrow(df), length(features_dict[:varnames]))
-X_features .= NaN
+outpath = "/media/teamlary/LabData/RobotTeam/finalized"
+if !ispath(outpath)
+    mkpath(outpath)
+    mkpath(joinpath(outpath, "11-23"))
+    mkpath(joinpath(outpath, "12-09"))
+    mkpath(joinpath(outpath, "12-10"))
+end
 
 
 function update_features!(X_features, df, collection_id)
@@ -33,7 +23,7 @@ function update_features!(X_features, df, collection_id)
         for f ∈ files
             if endswith(f, ".h5")
                 fpath = joinpath(root, f)
-                @info "Working on $(fpath)"
+                println("Working on $(fpath)")
                 h5open(fpath, "r") do h5
                     X_h5 = read(h5["data-Δx_0.1/X"])
                     Y_h5 = read(h5["data-Δx_0.1/Y"])
@@ -42,18 +32,23 @@ function update_features!(X_features, df, collection_id)
                     Xmin,Xmax = extrema(X_h5)
                     Ymin,Ymax = extrema(Y_h5)
 
+                    Data = read(h5["data-Δx_0.1/Data_μ"])
+
                     Xs = [x for x ∈ X_h5, y ∈ Y_h5]
                     Ys = [y for x ∈ X_h5, y ∈ Y_h5]
 
-                    @showprogress for i ∈ 1:nrow(df)
-                        row = @view df[i, :]
-                        if row.X ≥ Xmin && row.X ≤ Xmax && row.Y ≥ Ymin && row.Y ≤ Ymax
-                            idx = findfirst(row.X .== Xs .&& row.Y .== Ys)
-                            if IsInbounds[idx]
[…]

### 2023-08-20 utils/config.jl

@@ -1,10 +1,12 @@
 # basepath = "/media/jwaczak/Data/robotteam-data/raw"
-basepath = "/media/jwaczak/LabData/RobotTeam/raw/hsi"
+# basepath = "/media/jwaczak/LabData/RobotTeam/raw/hsi"
+basepath = "/media/teamlary/LabData/RobotTeam/raw/hsi"
 @assert ispath(basepath)
 
 
 # outpath = "/media/jwaczak/Data/robotteam-data/h5"
-outpath = "/media/jwaczak/LabData/RobotTeam/processed/hsi"
+# outpath = "/media/jwaczak/LabData/RobotTeam/processed/hsi"
+outpath = "/media/teamlary/LabData/RobotTeam/processed/hsi"
 if !ispath(outpath)
     mkpath(outpath)
 end
@@ -30,10 +32,10 @@ CollectionsDict = Dict(
         "Dye_1" => [],
         "Dye_2" => [],
     ),
-    "03-24" => Dict(
-        "Demonstration" => [],
-        "Demonstration_long" => [],
-    )
+    # "03-24" => Dict(
+    #     "Demonstration" => [],
+    #     "Demonstration_long" => [],
+    # )
 )
 
 
@@ -54,7 +56,7 @@ z_ground=292.0           # ground height (m)
 isflipped=false          # flip pixel orientation
 Δx = 0.10                # resampling resolution (m)
 is_spec_chunked=false    # chunk HDF5 by pixel
-is_band_chunked=true     # chunk HDF5 by band
+is_band_chunked=false    # chunk HDF5 by band
 
 
 # define bounding box for Scotty's Ranch

### 2023-08-21 3__colocate.jl
finished joining datasets

@@ -15,6 +15,7 @@ if !ispath(outpath)
     mkpath(joinpath(outpath, "11-23"))
     mkpath(joinpath(outpath, "12-09"))
     mkpath(joinpath(outpath, "12-10"))
+    mkpath(joinpath(outpath, "Full"))
 end
 
 
@@ -179,4 +180,25 @@ df_targets = df[idxs_notnans,:]
 CSV.write(joinpath(outpath, "12-10", "Targets.csv"), df_targets)
 CSV.write(joinpath(outpath, "12-10", "Features.csv"), df_features)
 
+
+
+
+# join together
+
+df_targets_1123 = CSV.read(joinpath(outpath, "11-23", "Targets.csv"), DataFrame)
+df_features_1123 = CSV.read(joinpath(outpath, "11-23", "Features.csv"), DataFrame)
+
+
+df_targets_1209 = CSV.read(joinpath(outpath, "12-09", "Targets.csv"), DataFrame)
+df_features_1209 = CSV.read(joinpath(outpath, "12-09", "Features.csv"), DataFrame)
+
+df_targets_1210 = CSV.read(joinpath(outpath, "12-10", "Targets.csv"), DataFrame)
+df_features_1210 = CSV.read(joinpath(outpath, "12-10", "Features.csv"), DataFrame)
+
+
+df_targets = vcat(df_targets_1123, df_targets_1209, df_targets_1210)
+df_features = vcat(df_features_1123, df_features_1209, df_features_1210)
+
+CSV.write(joinpath(outpath, "Full", "Targets.csv"), df_targets)
+CSV.write(joinpath(outpath, "Full", "Features.csv"), df_features)
 

### 2023-08-26 1d_datacub_viz.jl
3d visualizations

@@ -1,0 +1,29 @@
+using RobotTeam
+using HDF5
+using BenchmarkTools
+using CairoMakie
+using MintsMakieRecipes
+
+set_theme!(mints_theme)
+
+include("utils/vis_tools.jl")
+include("utils/config.jl")
+
+basepath
+
+files = get_raw_file_list.(get_bil_files(basepath, "Scotty_1"))
+
+f = files[1]
+
+
+hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
+xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ = resample_datacube_fast(hsi; Δx=Δx)
+
+
+
+# plot pre-georectified HSI
+
+# plot georectified HSI
+
+# plot HSI on map
+

### 2023-08-26 1e_datacube-3d-vis.jl

@@ -1,0 +1,122 @@
+using RobotTeam
+using HDF5
+using BenchmarkTools
+using GLMakie, GeometryBasics
+using MintsMakieRecipes
+
+set_theme!(mints_theme)
+
+include("utils/vis_tools.jl")
+include("utils/config.jl")
+
+basepath
+
+files = get_raw_file_list.(get_bil_files(basepath, "Scotty_1"))
+
+f = files[1]
+
+
+hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
+
+
+size(hsi.Reflectance)
+
+data = PermutedDimsArray(hsi.Reflectance, (2,3,1))
+
+# make sure to clip to reasonable values
+Rmin = minimum(data)
+Rmax = maximum(data)
+cg = cgrad(:inferno, range(Rmin, stop=Rmax, length=256))
+
+
+size(data)
+
+heatmap(z₊)
+
+heatmap(data[1,:,:])
+
+size(y₋)
+size(x₋)
+
+y₋ = [cg[data[i,1,k]] for i in axes(data,1), k in axes(data,3)][:, end:-1:1]
+y₊ = [cg[data[i,end,k]] for i in axes(data,1), k in axes(data,3)][:, :]
+y_∅ = [RGBA(0,0,0,0) for i in axes(data,1), k in axes(data,3)]
+
+x₋ = [cg[data[1,j,k]] for j in axes(data,2), k in axes(data,3)][:,end:-1:1]
+x₊ = [cg[data[end,j,k]] for j in axes(data,2), k in axes(data,3)][:,end:-1:1]
+x_∅ = [RGBA(0,0,0,0) for j in axes(data,2), k in axes(data,3)]
+
+z₋ = [cg[data[i,j,300]] for i in axes(data,1), j in axes(data,2)][end:-1:1,:]
+z₊ = getRGB(hsi)[end:-1:1,:]
+z_∅ = [RGBA(0,0,0,0) for i in axes(data,1), j in axes(data,2)]
+
+function meshcube(o=Vec3f(0), sizexyz = Vec3f(1))
+    uvs = map(v -> v ./ (3, 2), Vec2f[
+        (0, 0), (0, 1), (1, 1), (1, 0),
+        (1, 0), (1, 1), (2, 1), (2, 0),
[…]

### 2023-08-28 1e_datacube-3d-vis.jl
got the 3d plots working

@@ -3,120 +3,83 @@ using HDF5
 using BenchmarkTools
 using GLMakie, GeometryBasics
 using MintsMakieRecipes
+using ProgressMeter
 
 set_theme!(mints_theme)
 
 include("utils/vis_tools.jl")
 include("utils/config.jl")
 
+
+
 basepath
 
-files = get_raw_file_list.(get_bil_files(basepath, "Scotty_1"))
+# files = get_raw_file_list.(get_bil_files(joinpath(basepath, "11-23"), "Scotty_1"))
+# f = files[1]
 
-f = files[1]
+
+
+files = get_raw_file_list.(get_bil_files(joinpath(basepath, "12-09"), "Dye_1"))
+f = files[6]
 
 
 hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
+img = getRGB(hsi)
+fig, ax, hm = heatmap(img)
+
+size(img)
 
 
-size(hsi.Reflectance)
-
-data = PermutedDimsArray(hsi.Reflectance, (2,3,1))
-
-# make sure to clip to reasonable values
-Rmin = minimum(data)
-Rmax = maximum(data)
-cg = cgrad(:inferno, range(Rmin, stop=Rmax, length=256))
-
-
-size(data)
-
-heatmap(z₊)
-
-heatmap(data[1,:,:])
-
-size(y₋)
-size(x₋)
-
-y₋ = [cg[data[i,1,k]] for i in axes(data,1), k in axes(data,3)][:, end:-1:1]
-y₊ = [cg[data[i,end,k]] for i in axes(data,1), k in axes(data,3)][:, :]
-y_∅ = [RGBA(0,0,0,0) for i in axes(data,1), k in axes(data,3)]
-
-x₋ = [cg[data[1,j,k]] for j in axes(data,2), k in axes(data,3)][:,end:-1:1]
-x₊ = [cg[data[end,j,k]] for j in axes(data,2), k in axes(data,3)][:,end:-1:1]
-x_∅ = [RGBA(0,0,0,0) for j in axes(data,2), k in axes(data,3)]
-
-z₋ = [cg[data[i,j,300]] for i in axes(data,1), j in axes(data,2)][end:-1:1,:]
-z₊ = getRGB(hsi)[end:-1:1,:]
[…]

### 2023-08-28 src/RobotTeam.jl

@@ -34,10 +34,7 @@ export importAirMar, importCOM1, importCOM2, importCOM3, importLISST, importNMEA
 
 include("visualization.jl")
 using .Visualization
-export process_image, generateRGB!, getRGB
-
-
-
+export process_image, generateRGB!, getRGB, vis_cube
 
 
 end

### 2023-08-28 src/visualization.jl

@@ -4,11 +4,14 @@ using ..ENVI: HyperspectralImage
 
 using Images
 using HDF5
-
+using GLMakie
+using GeometryBasics
 
 export process_image
 export generateRGB!
 export getRGB
+export vis_cube
+
 
 function process_image(img;α=10.0,β=0.0)
     # see example: https://www.satmapper.hu/en/rgb-images/
@@ -92,6 +95,122 @@ end
 
 
 
+
+
+
+function meshcube(o=Vec3f(0), sizexyz=Vec3f(1))
+    uvs = map(v -> v ./ (3, 2), Vec2f[
+        (0, 0), (0, 1), (1, 1), (1, 0),
+        (1, 0), (1, 1), (2, 1), (2, 0),
+        (2, 0), (2, 1), (3, 1), (3, 0),
+        (0, 1), (0, 2), (1, 2), (1, 1),
+        (1, 1), (1, 2), (2, 2), (2, 1),
+        (2, 1), (2, 2), (3, 2), (3, 1),
+    ])
+    m = normal_mesh(Rect3f(Vec3f(-0.5) .+ o, sizexyz))
+    m = GeometryBasics.Mesh(meta(coordinates(m);
+            uv=uvs, normals=normals(m)), faces(m))
+end
+
+
+
+
+
+function vis_cube(hsi; cmap=:rainbow, offset=0.0, shading=false, ibounds=(1,1), jbounds=(1,1))
+    size(hsi.Reflectance)
+
+    data = PermutedDimsArray(hsi.Reflectance, (2, 3, 1))
+    if ibounds != (1,1)
+        imin,imax = ibounds
+        data = data[imin:imax,:,:]
+    end
+
+    if jbounds != (1,1)
+        jmin,jmax=jbounds
+        data = data[:,jmin:jmax,:]
+    end
+
+
+
+    # make sure to clip to reasonable values
+    Rmin = minimum(data)
+    Rmax = maximum(data)
+
+    cg = cgrad(cmap, range(Rmin, stop=Rmax, length=256))
+
+    y₋ = [cg[data[i, 1, k] + offset] for i in axes(data, 1), k in axes(data, 3)][:, end:-1:1]
+    y₊ = [cg[data[i, end, k] + offset] for i in axes(data, 1), k in axes(data, 3)][:, :]
[…]

### 2023-08-28 paper/paper.tex
Updates from Overleaf

@@
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+\subsection{Reflectance Conversion}
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+Here we can detail the conversion from radiance to reflectance using the downwelling irradiance spectrum with the assumption of a Lambertian surface.
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+\begin{figure}[H]
+    \centering
+    \includegraphics{./assets/radiance.eps}
+    \caption{Radiance spectrum captured for single HSI pixel.}
+    \label{fig:radiance}
+\end{figure}
+
+\subsection{Georectification Procedure}
 
@@
 \section{Results}
-\begin{list}
-    \bullet Create table with processing timings for each step on a typical HSI
-    \bullet Create second table comparing time for full processing including resampling to a variety of scales (e.g.
-5 cm, 10 cm, 25 cm) We will want a version of the processing function that does not include the uncertainties and the spectral indices
-    \bullet create additional table showing size of each of the data producs and their step in the pipeline (ending with a dataproduct like the NDVI)
-    \bullet Create a figure showing the georeferenced image on top of the satellite background 
-    \bullet Create another figure of the entire map with a spectral index applied to one of the dye-release datasets (to demonstrate use for real-time application like oil-spill)
-    \bullet create a figure of a sample HSI datacube in 3-d like from the previous paper with the rgb image on the top. 
-\end{list}
-
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
-
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
-
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
-
-The text continues here.
-
-\subsection{Figures, Tables and Schemes}
-
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
 
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
+    \includegraphics[width=10.5 cm]{./figures/timing.eps}
 \caption{This is a figure.
@@
 \end{figure}
-\unskip
+
+NOTE: we need to update these timings by first copying the HSI to the local drive (off of the external hard drive). This will probably have some effect on the read/write speeds for the test.
 
 \begin{table}[H] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
+\caption{Resampling times as a function of pixel resolution.\label{tab1}}
 \newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
+\begin{tabularx}{\textwidth}{CC}
 \toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+\textbf{Resolution (m)}	& \textbf{Execution time (s)}\\
 \midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data \textsuperscript{1}\\
+0.5		&   1.328	\\
+0.25    &   1.547	\\
+0.1     &   3.557   \\
+0.05    &   9.235   \\
 \bottomrule
 \end{tabularx}
-\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
 \end{table}
 
-The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).
-
-% Example of a figure that spans the whole page width. The same concept works for tables, too.
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
-\end{adjustwidth}
-\caption{This is a wide figure.\label{fig2}}
-\end{figure}
-
-\begin{table}[H]
-\caption{This is a wide table.\label{tab2}}
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{CCCC}
-			\toprule
-			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
-			\midrule
-\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
-			  	                   & Data			& Data			& Data\\
-			             	      & Data			& Data			& Data\\
-                   \midrule
-\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
-			  	                  & Data			& Data			& Data\\
-			             	     & Data			& Data			& Data\\
-                   \midrule
-\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
-			  	                 & Data			& Data			& Data\\
-			             	    & Data			& Data			& Data\\
-                  \midrule
-\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
-			  	                 & Data			& Data			& Data\\
-			             	    & Data			& Data			& Data\\
-			\bottomrule
-		\end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{* Tables may have a footer.}}
-\end{table}
-
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
-
-Text.
-
-Text.
-
-\subsection{Formatting of Mathematical Components}
-
-This is the example 1 of equation:
-\begin{linenomath}
-\begin{equation}
-a = 1,
-\end{equation}
-\end{linenomath}
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-This is the example 2 of equation:
-\begin{adjustwidth}{-\extralength}{0cm}
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
-\end{adjustwidth}
-
-% Example of a page in landscape format (with table and table footnote).
-%\startlandscape
-%\begin{table}[H] %% Table in wide page
-%\caption{This is a very wide table.\label{tab3}}
-%	\begin{tabularx}{\textwidth}{CCCC}
-%		\toprule
-%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
-%		\midrule
-%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
-%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
-%		\bottomrule
-%	\end{tabularx}
-%	\begin{adjustwidth}{+\extralength}{0cm}
-%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
-%	\end{adjustwidth}
-%\end{table}
-%\finishlandscape
-
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+\textbf{NOTE} Stuff to do in this section:
+\begin{itemize}
+    \item  Create table with processing timings for each step on a typical HSI
+    \item Create second table comparing time for full processing including resampling to a variety of scales (e.g.
+5 cm, 10 cm, 25 cm) We will want a version of the processing function that does not include the uncertainties and the spectral indices
+    \item create additional table showing size of each of the data producs and their step in the pipeline (ending with a dataproduct like the NDVI)
+    \item Create a figure showing the georeferenced image on top of the satellite background 
+    \item Create another figure of the entire map with a spectral index applied to one of the dye-release datasets (to demonstrate use for real-time application like oil-spill)
+    \item create a figure of a sample HSI datacube in 3-d like from the previous paper with the rgb image on the top. 
+\end{itemize}
 

### 2023-08-28 paper/paper.tex

@@
 
+\textbf{NOTE:} we should update the following three figures to make a single figure with the radiances/irradiance in on the left (using the left and right y-axis) and the reflectance on the right.
+
 \begin{figure}[H]
     \centering
-    \includegraphics{./assets/radiance.eps}
+    \includegraphics[width=10.5cm]{./assets/radiance.eps}
     \caption{Radiance spectrum captured for single HSI pixel.}
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=10.5cm]{./assets/solar_irradiance.eps}
+    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
+    \label{fig:solar-irradiance}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=10.5cm]{./assets/reflectance_rainbow.eps}
+    \caption{Resuliting reflectance spectrum.}
+    \label{fig:reflectance}
+\end{figure}
+
 \subsection{Georectification Procedure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=10.5cm]{./assets/georectification.svg}
+    \caption{Georectification procedure.}
+    \label{fig:georectification}
+\end{figure}
 

### 2023-08-29 1e_datacube-3d-vis.jl
got colormap working!

@@ -30,7 +30,9 @@ fig, ax, hm = heatmap(img)
 size(img)
 
 
-fig = vis_cube(hsi; cmap=:batlow, offset=0.0, ibounds=(250,1600))
+# heatmap(log10.(hsi.Reflectance[:,:,1]))
+
+fig = vis_cube(hsi; cmap=:jet, offset=0.1, ibounds=(250,1600))
 save("demo-cube.png", fig)
 
 
@@ -42,14 +44,23 @@ xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, 
 
 data = PermutedDimsArray(Data_μ[1:462,:,:], (2, 3, 1))
 
+ij_pixels = findall(IsInbounds[1:462,:,:])
 
+offset = 0.1
+data = log10.(data .+ offset)
+# dmin, dmax = extrema(data[ij_pixels])
+# data .= (data .- dmin) ./ (dmax = dmin)
+
+# cg = cgrad(:jet)
+
+size(data)
+data_plot = @view data[100:end,:,:]
 
 fig = Figure(; resolution=(1200,600))
 ax = Axis3(fig[1, 1],
-           # aspect=:data,
-           #xgridvisible=false,
-           #ygridvisible=false,
            perspectiveness=1,
+           elevation=3π/16-π/32,
+           azimuth=3π/4
            )
 hidedecorations!(ax)
 hidespines!(ax)
@@ -59,9 +70,10 @@ hidespines!(ax)
     mesh!(
         ax,
         mr;
-        color = data[:,:,k],
+        color = data_plot[:,:,k],
         interpolate=false,
-        colormap = :rainbow,
+        colormap = :jet,
+        shading=false
         )
 
 end
@@ -69,13 +81,15 @@ end
 ij_pixels = findall(IsInbounds)
 Ref_img = getRGB(Data_μ, λs, ij_pixels)
 
+Ref_img = Ref_img[100:end, :]
+
 mr = Rect3f(Vec3f(0,0,462*Δx), Vec3f(length(xs)*Δx, length(ys)*Δx, Δx))
 mesh!(
     ax,
     mr;
     color= Ref_img,
     interpolate=false,
-    colormap = :rainbow,
+    shading=false,
 )
 
 save("demo-rectified-cube.png", fig)

### 2023-08-29 src/visualization.jl

@@ -116,38 +116,41 @@ end
 
 
 
-function vis_cube(hsi; cmap=:rainbow, offset=0.0, shading=false, ibounds=(1,1), jbounds=(1,1))
+function vis_cube(hsi; cmap=:rainbow, offset=0.1, shading=false, ibounds=(1,1), jbounds=(1,1))
     size(hsi.Reflectance)
 
-    data = PermutedDimsArray(hsi.Reflectance, (2, 3, 1))
-    if ibounds != (1,1)
-        imin,imax = ibounds
-        data = data[imin:imax,:,:]
+    data = log10.(permutedims(hsi.Reflectance .+ offset, (2, 3, 1)))
+    dmin, dmax = extrema(data)
+
+    data .= (data .- dmin) ./ (dmax - dmin)
+
+    println(extrema(data))
+
+    if ibounds != (1, 1)
+        imin, imax = ibounds
+        data = data[imin:imax, :, :]
     end
 
-    if jbounds != (1,1)
-        jmin,jmax=jbounds
-        data = data[:,jmin:jmax,:]
+    if jbounds != (1, 1)
+        jmin, jmax = jbounds
+        data = data[:, jmin:jmax, :]
     end
 
 
 
-    # make sure to clip to reasonable values
-    Rmin = minimum(data)
-    Rmax = maximum(data)
+    cg = cgrad(cmap)
 
-    cg = cgrad(cmap, range(Rmin, stop=Rmax, length=256))
-
-    y₋ = [cg[data[i, 1, k] + offset] for i in axes(data, 1), k in axes(data, 3)][:, end:-1:1]
-    y₊ = [cg[data[i, end, k] + offset] for i in axes(data, 1), k in axes(data, 3)][:, :]
+    y₋ = [cg[data[i, 1, k]] for i in axes(data, 1), k in axes(data, 3)][:, end:-1:1]
+    y₊ = [cg[data[i, end, k]] for i in axes(data, 1), k in axes(data, 3)][:, :]
     y_∅ = [RGBA(0, 0, 0, 0) for i in axes(data, 1), k in axes(data, 3)]
 
-    x₋ = [cg[data[1, j, k] + offset] for j in axes(data, 2), k in axes(data, 3)][end:-1:1, end:-1:1]
-    x₊ = [cg[data[end, j, k] + offset] for j in axes(data, 2), k in axes(data, 3)][:, end:-1:1]
[…]

### 2023-08-29 paper/paper.tex

@@
     \centering
-    \includegraphics[width=10.5cm]{./assets/georectification.svg}
-    \caption{Georectification procedure.}
+    \includegraphics[width=10.5cm]{./assets/georectification.eps}
+    \caption{Visual representation of scan-line geometry for the drone based hyperspectral imaging platform.}
     \label{fig:georectification}
@@
 5 cm, 10 cm, 25 cm) We will want a version of the processing function that does not include the uncertainties and the spectral indices
-    \item create additional table showing size of each of the data producs and their step in the pipeline (ending with a dataproduct like the NDVI)
+    \item create pipeline visualization showing size of each of the data products and their step in the pipeline (ending with a dataproduct like the NDVI)
     \item Create a figure showing the georeferenced image on top of the satellite background 

### 2023-08-30 1e_datacube-3d-vis.jl
updated datacube for georectified version

@@ -12,88 +12,44 @@ include("utils/config.jl")
 
 
 
-basepath
-
-# files = get_raw_file_list.(get_bil_files(joinpath(basepath, "11-23"), "Scotty_1"))
-# f = files[1]
+basepath = "/home/teamlary/gitrepos/utd/RobotTeam.jl/data/raw"
+f = get_raw_file_list(get_bil_files(basepath, "Dye_1")[1])
 
 
-
-files = get_raw_file_list.(get_bil_files(joinpath(basepath, "12-09"), "Dye_1"))
-f = files[6]
-
-
+# read in the HSI
 hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
+
 img = getRGB(hsi)
 fig, ax, hm = heatmap(img)
-
 size(img)
 
 
-# heatmap(log10.(hsi.Reflectance[:,:,1]))
-
-fig = vis_cube(hsi; cmap=:jet, offset=0.1, ibounds=(250,1600))
-save("demo-cube.png", fig)
 
 
+
+# 1. create visualization of un-georectified HSI
+size_in_inches = (3, 3)
+dpi = 400
+size_in_pixels = size_in_inches .* dpi
+
+fig = vis_cube(hsi; cmap=:jet, offset=0.1, ibounds=(250,1600), resolution=size_in_pixels)
+
+save("./paper/figures/demo-cube.png", fig)
+
+
+# 2. create visualization of georectified HSI
 
 # now let's visualize the georectified cube
-
 xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ = resample_datacube_fast(hsi; Δx=Δx)
 
 
-data = PermutedDimsArray(Data_μ[1:462,:,:], (2, 3, 1))
+fig = vis_rectified_cube(Data_μ, xs, ys, IsInbounds, λs, Δx; offset=0.0, ibounds=(100, length(xs)), resolution=size_in_pixels, colorbar=true)
 
-ij_pixels = findall(IsInbounds[1:462,:,:])
-
-offset = 0.1
-data = log10.(data .+ offset)
-# dmin, dmax = extrema(data[ij_pixels])
-# data .= (data .- dmin) ./ (dmax = dmin)
-
-# cg = cgrad(:jet)
-
-size(data)
-data_plot = @view data[100:end,:,:]
[…]

### 2023-08-30 src/RobotTeam.jl

@@ -34,7 +34,6 @@ export importAirMar, importCOM1, importCOM2, importCOM3, importLISST, importNMEA
 
 include("visualization.jl")
 using .Visualization
-export process_image, generateRGB!, getRGB, vis_cube
-
+export process_image, getRGB, vis_cube, vis_rectified_cube
 
 end

### 2023-08-30 src/visualization.jl

@@ -6,12 +6,13 @@ using Images
 using HDF5
 using GLMakie
 using GeometryBasics
+using ProgressMeter
+using Statistics
 
 export process_image
-export generateRGB!
 export getRGB
 export vis_cube
-
+export vis_rectified_cube
 
 function process_image(img;α=10.0,β=0.0)
     # see example: https://www.satmapper.hu/en/rgb-images/
@@ -116,7 +117,7 @@ end
 
 
 
-function vis_cube(hsi; cmap=:rainbow, offset=0.1, shading=false, ibounds=(1,1), jbounds=(1,1))
+function vis_cube(hsi; cmap=:jet, offset=0.1, shading=false, ibounds=(1,1), jbounds=(1,1), resolution=(800,600), azimuth=-π/4, elevation=3π/16)
     size(hsi.Reflectance)
 
     data = log10.(permutedims(hsi.Reflectance .+ offset, (2, 3, 1)))
@@ -196,14 +197,15 @@ function vis_cube(hsi; cmap=:rainbow, offset=0.1, shading=false, ibounds=(1,1), 
     ]
 
 
-    fig = Figure(; resolution=(1200, 600))
+    fig = Figure(; resolution=resolution, backgroundcolor=RGBA(0,0,0,0))
     ax = Axis3(
         fig[1, 1],
         aspect=:data,
         xgridvisible=false,
         ygridvisible=false,
         perspectiveness=1,
-        elevation = 3π / 16,
+        elevation = elevation,
+        azimuth = azimuth,
     )
     hidedecorations!(ax)
     hidespines!(ax)
@@ -217,6 +219,86 @@ function vis_cube(hsi; cmap=:rainbow, offset=0.1, shading=false, ibounds=(1,1), 
     return fig
 end
 
+
+
+function vis_rectified_cube(Data_μ, xs, ys, IsInbounds, λs, Δx; ibounds=(1, 1), jbounds=(1, 1), offset = 0.1, colormap=:jet, resolution=(800, 600), azimuth=3π / 4, elevation=3π / 16, colorbar=false)
+
+    nλs = length(λs)
+
+    println("\tGenerating RGB view...")
+    ij_pixels = findall(IsInbounds)
+    Ref_img = getRGB(Data_μ, λs, ij_pixels)
+
+    println("\tReshaping data for plotting...")
+    data = PermutedDimsArray(Data_μ[1:nλs, :, :], (2, 3, 1))
+
+    println("\tApplying log10...")
[…]

### 2023-08-30 paper/paper.tex
added preliminary datacube plot
updated the timings benchmarks with more datacubes

@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=10.5cm]{./figures/demo-rectified-cube.png}
+    \caption{Georectified Hyperspectral Datacube}
+    \label{fig:rectified-cube}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure}[H]
-    \includegraphics[width=10.5 cm]{./figures/timing.eps}
+    \includegraphics[width=10.5 cm]{./figures/regrid-timing.eps}
 \caption{This is a figure.
@@
 Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
+A caption on a single line should be centered.\label{fig-regridding-timing}}
+\end{figure}
+
+\begin{figure}[H]
+  \includegraphics[width=10.5 cm]{./figures/reflectance-timing.eps}
+  \caption{Description \label{fig-reflectance-timing}}
 \end{figure}
@@
 0.05    &   9.235   \\
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{table}[H]
+  \caption{Loading and Reflectance Conversion Times.\label{tab1}}
+  \newcolumntype{C}{>{\centering\arraybackslash}X}
+  \begin{tabularx}{\textwidth}{CC}
+    \toprule
+    \textbf{Number of scan lines}	& \textbf{Execution time (s)}\\
+    \midrule
+    371		&   2.049	\\
+    725    &   4.219	\\
+    1000     &   5.875   \\
     \bottomrule

### 2023-08-30 1c_timing-tests.jl

@@ -9,31 +9,16 @@ set_theme!(mints_theme)
 include("utils/vis_tools.jl")
 include("utils/config.jl")
 
-basepath
 
-files = get_raw_file_list.(get_bil_files(basepath, "Scotty_1"))
+basepath = "/home/teamlary/gitrepos/utd/RobotTeam.jl/data/raw"
+f1 = get_raw_file_list(get_bil_files(basepath, "Dye_1")[1])
+f2 = get_raw_file_list(get_bil_files(basepath, "NoDye_1")[1])
+f3 = get_raw_file_list(get_bil_files(basepath, "Scotty_1")[1])
 
-f = files[1]
+f = f3
 
-f
 
 hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
-
-hsi_benchmark = @benchmark HyperspectralImage($f.bilpath, $f.bilhdr, $f.lcfpath, $f.timespath, $f.specpath, $f.spechdr; isflipped=true);
-
-
-
-
-# xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ, Data_σ = resample_datacube(hsi; Δx=Δx)
-xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ = resample_datacube_fast(hsi; Δx=Δx)
-
-
-resample_benchmark = @benchmark resample_datacube_fast($hsi; Δx=$Δx)
-
-mean(hsi_benchmark)
-mean(resample_benchmark)
-
-
 
 
 suite = BenchmarkGroup()
@@ -41,7 +26,10 @@ suite = BenchmarkGroup()
 suite["reflectance-conversion"] = BenchmarkGroup()
 suite["resampling"] = BenchmarkGroup()
 
-suite["reflectance-conversion"]["Scotty_1-1"] = @benchmarkable HyperspectralImage($f.bilpath, $f.bilhdr, $f.lcfpath, $f.timespath, $f.specpath, $f.spechdr; isflipped=true)
+suite["reflectance-conversion"]["Dye_1"] = @benchmarkable HyperspectralImage($f1.bilpath, $f1.bilhdr, $f1.lcfpath, $f1.timespath, $f1.specpath, $f1.spechdr; isflipped=true)
[…]

### 2023-08-30 1e_datacube-3d-vis.jl
added new figures for the reflectance at the arrow

@@ -4,6 +4,7 @@ using BenchmarkTools
 using GLMakie, GeometryBasics
 using MintsMakieRecipes
 using ProgressMeter
+using Statistics
 
 set_theme!(mints_theme)
 
@@ -25,11 +26,19 @@ size(img)
 
 
 
+my_theme = mints_theme
+my_theme.Axis.xticklabelsize=17
+my_theme.Axis.yticklabelsize=17
+my_theme.Axis.xlabelsize=20
+my_theme.Axis.ylabelsize=20
+my_theme.Axis.titlesize=22
+set_theme!(my_theme)
+
 
 
 # 1. create visualization of un-georectified HSI
 size_in_inches = (3, 3)
-dpi = 400
+dpi = 600
 size_in_pixels = size_in_inches .* dpi
 
 fig = vis_cube(hsi; cmap=:jet, offset=0.1, ibounds=(250,1600), resolution=size_in_pixels)
@@ -45,11 +54,47 @@ xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, 
 
 fig = vis_rectified_cube(Data_μ, xs, ys, IsInbounds, λs, Δx; offset=0.0, ibounds=(100, length(xs)), resolution=size_in_pixels, colorbar=true)
 
-colgap!(fig.layout, -150)
+colgap!(fig.layout, -300)
 
 fig
 
-save("./paper/demo-rectified-cube.png", fig)
+save("./paper/figures/demo-rectified-cube.png", fig)
+
+
+ax = current_axis(fig)
+
+arrows!([(length(xs)-250)*Δx],[(length(ys))*Δx],[Δx*(-60)],[0],[0],[50*Δx]; arrowsize=1)
+
+
+save("./paper/figures/rectified-cube-w-arrow.png", fig)
+
+fig
+
+# plot reflectance of slice through the plume
+using CairoMakie
+
+data = log10.(Data_μ[1:462,:,:])
+idx_not_nan_or_inf = findall(.!(isnan.(data)) .&& .!(isinf.(data)))
+Rmin = quantile(data[idx_not_nan_or_inf], 0.1)
+Rmax = quantile(data[idx_not_nan_or_inf], 0.99)
+
+fig2 = Figure();
+ax = GLMakie.Axis(fig2[1,1], xlabel="λ (nm)", ylabel="Reflectance");
[…]

### 2023-08-30 1d_datacub_viz.jl
added plot of single georectified HSI

@@ -6,24 +6,73 @@ using MintsMakieRecipes
 
 set_theme!(mints_theme)
 
+my_theme = mints_theme
+my_theme.Axis.xticklabelsize=17
+my_theme.Axis.yticklabelsize=17
+my_theme.Axis.xlabelsize=20
+my_theme.Axis.ylabelsize=20
+my_theme.Axis.titlesize=22
+set_theme!(my_theme)
+
+
 include("utils/vis_tools.jl")
 include("utils/config.jl")
 
+
+
+
 basepath
 
-files = get_raw_file_list.(get_bil_files(basepath, "Scotty_1"))
 
-f = files[1]
-
-
-hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
-xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ = resample_datacube_fast(hsi; Δx=Δx)
-
+# create a plot of the HSI path on a satellite background tile
+w= -97.717472
+n= 33.703572
+s= 33.700797
+e= -97.712413
 
 
-# plot pre-georectified HSI
+satmap = get_background_satmap(w,e,s,n)
 
-# plot georectified HSI
 
-# plot HSI on map
+h5path = joinpath(outpath, "12-09", "Dye_1", "Dye_1-6.h5")
+@assert isfile(h5path)
+
+
+h5 = h5open(h5path, "r")
+
+Latitudes = read(h5["data-Δx_0.1/Latitudes"])
+Longitudes = read(h5["data-Δx_0.1/Longitudes"])
+Data_μ = read(h5["data-Δx_0.1/Data_μ"])
+varnames = read(h5["data-Δx_0.1/varnames"])
+printnames = read(h5["data-Δx_0.1/printnames"])
+
+
+indices_metrics = findfirst(x-> x=="mNDWI", varnames):length(varnames)
+
+
+size_in_inches = (4, 3)
+dpi = 300
+size_in_pixels = size_in_inches .* dpi
+
+fig = Figure(;resolution=size_in_pixels)
+ax = CairoMakie.Axis(fig[1,1], xlabel="Longitude", ylabel="Latitude")
+hm = heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img)
+
+rgb = getRGB(h5)
[…]

### 2023-08-31 1d_datacub_viz.jl
added updated spectra plots

@@ -45,10 +45,12 @@ Longitudes = read(h5["data-Δx_0.1/Longitudes"])
 Data_μ = read(h5["data-Δx_0.1/Data_μ"])
 varnames = read(h5["data-Δx_0.1/varnames"])
 printnames = read(h5["data-Δx_0.1/printnames"])
+λs = read(h5["data-Δx_0.1/λs"])
 
 
 indices_metrics = findfirst(x-> x=="mNDWI", varnames):length(varnames)
 
+spec_R = Data_μ[1:]
 
 size_in_inches = (4, 3)
 dpi = 300
@@ -68,8 +70,93 @@ save("./paper/figures/georectified-hsi-plume.png", fig)
 
 fig
 
-# plot radiance, irradiance, and reflectance for single HSI (12-09 Dye_1-6) for a slice from the plume
+close(h5)
 
+# plot radiance, irradiance, and reflectance for single HSI (12-09 Dye_1-6) for a slice from the plume
+fpath = "/media/teamlary/LabData/RobotTeam/raw/hsi/12-09/Dye_1-6"
+readdir(fpath)
+@assert ispath(fpath)
+
+rad_dat = zeros(UInt16, length(λs))
+ref_dat = zeros(Float64, length(λs))
+let
+    dat, h, p = read_envi_file(joinpath(fpath, "Dye_1_Pika_XC2_6-radiance.bil"), joinpath(fpath, "Dye_1_Pika_XC2_6-radiance.bil.hdr"))
+    rad_dat .= dat[:, 100, 100]
+end
+
+fnames = joinpath.(fpath, readdir(fpath))
+
+let
+    hsi = HyperspectralImage(
+        fnames[1],
+        fnames[2],
+        fnames[4],
+        fnames[3],
+        fnames[5],
+        fnames[6];
+        isflipped=true
+    );
+
+    ref_dat .= hsi.Reflectance[1:length(λs), 100, 100]
+end
+
+
+irrad_dat = zeros(Float64, 2048)
+λs_irrad = zeros(Float64, 2048)
+let
+    dat, h, p = read_envi_file(fnames[5], fnames[6])
+    irrad_dat .= vec(dat)
+    λs_irrad .= p["wavelengths"]
+end
+
+
+fig = Figure()
[…]

### 2023-09-01 1d_datacub_viz.jl
updating with maps of spectral indices

@@ -159,7 +159,78 @@ save("./paper/figures/reflectance-sample.pdf", fig)
 fig
 
 # plot single HSI on map (1209 Dye_1-6)
+varnames[indices_metrics[1]]
+m1 = Data_μ[indices_metrics[1],:,:]
 
-# plot spectral indices filtered to water-only pixels
+thresh_h2o = 0.25
+idxs_h2o = findall(m1 .≥ thresh_h2o)
+idxs_land = findall(m1 .< thresh_h2o)
+
+m1[idxs_land] .= NaN
+
+fig = Figure(;resolution=size_in_pixels);
+ax = CairoMakie.Axis(fig[1,1], xlabel="Longitude", ylabel="Latitude", title=printnames[indices_metrics[1]]);
+hm = heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img)
+hm2 = heatmap!(ax, Longitudes, Latitudes, m1, clims=metric_bounds[varnames[indices_metrics[1]]])
+fig
+
+
+# loop through and make maps
+for (day, runs) ∈ CollectionsDict
+    for (run, fs) ∈ runs
+        println("Working on $run")
+
+        savepath = joinpath(outpath, day, run, "maps")
+        if !ispath(savepath)
+            mkpath(savepath)
+        end
+
+        # loop over all metrics
+        for idx ∈ indices_metrics
+            println("\t$(printnames[idx])")
+
+            # set up plot
+            size_in_inches = (4, 3)
+            dpi = 400
+            size_in_pixels = size_in_inches .* dpi
+            f = Figure(resolution=size_in_pixels)
+            ax = CairoMakie.Axis(f[1,1], xlabel="longitude", ylabel="latitude", title="$day")
+            heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img)
+            xlims!(ax, -97.7168, -97.7125)
+            ylims!(ax, 33.70075, 33.7035)
+
+            # loop over each file in the run and add the values
+            for f ∈ fs
+                fname = split(f.lcfpath, "/")[end-1]
+                h5path = joinpath(outpath, day, run, fname * ".h5")
+                println("\t\tplotting $(h5path)")
+
+                try
+                    h5open(h5path, "r") do h5
+                        Latitudes = h5["data-Δx_$(Δx)/Latitudes"][:,:]
[…]

### 2023-09-01 utils/vis_tools.jl

@@ -46,3 +46,29 @@ function get_background_satmap(w::Float64, e::Float64, s::Float64, n::Float64; o
     )
 end
 
+
+
+# metric bounds
+metric_bounds = Dict(
+    "mNDWI" => (-1, 1),
+    "NDVI" => (-1 ,1),
+    "SR" => (0, 30),
+    "EVI" => (-1, 1),
+    "AVRI" => (-1, 1),
+    "NDVI_705" => (-1,1),
+    "MSR_705" => (0, 30),
+    "MNDVI" => (-1, 1),
+    "VOG1" => (0, 20),
+    "VOG2" => (0, 20),
+    "VOG3" => (0, 20),
+    "PRI" => (-1,1),
+    "SIPI" => (0, 2),
+    "PSRI" => (-1, 1),
+    "CRI1" => (0, 15),
+    "CRI2" => (0, 15),
+    "ARI1" => (0, 0.2),
+    "ARI2" => (0, 0.2),
+    "WBI" => (0.5, 1.5),
+    "MCRI" => (0, 15),
+    "TCARI" => (0, 15)
+)

### 2023-09-03 1d_datacub_viz.jl
working on figures

@@ -50,7 +50,6 @@ printnames = read(h5["data-Δx_0.1/printnames"])
 
 indices_metrics = findfirst(x-> x=="mNDWI", varnames):length(varnames)
 
-spec_R = Data_μ[1:]
 
 size_in_inches = (4, 3)
 dpi = 300
@@ -187,6 +186,8 @@ for (day, runs) ∈ CollectionsDict
 
         # loop over all metrics
         for idx ∈ indices_metrics
+            GC.gc()
+
             println("\t$(printnames[idx])")
 
             # set up plot

### 2023-09-04 1d_datacub_viz.jl
added new plots

@@ -55,7 +55,7 @@ size_in_inches = (4, 3)
 dpi = 300
 size_in_pixels = size_in_inches .* dpi
 
-fig = Figure(;resolution=size_in_pixels)
+fig = Figure(;resolution=size_in_pixels, figure_padding=50)
 ax = CairoMakie.Axis(fig[1,1], xlabel="Longitude", ylabel="Latitude")
 hm = heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img)
 
@@ -64,6 +64,8 @@ hm_rgb = heatmap!(ax, Longitudes, Latitudes, rgb)
 
 xlims!(ax, -97.717, -97.715)
 ylims!(ax, 33.7015, 33.7025)
+
+fig
 
 save("./paper/figures/georectified-hsi-plume.png", fig)
 
@@ -174,64 +176,150 @@ hm2 = heatmap!(ax, Longitudes, Latitudes, m1, clims=metric_bounds[varnames[indic
 fig
 
 
-# loop through and make maps
-for (day, runs) ∈ CollectionsDict
-    for (run, fs) ∈ runs
-        println("Working on $run")
 
-        savepath = joinpath(outpath, day, run, "maps")
-        if !ispath(savepath)
-            mkpath(savepath)
-        end
 
-        # loop over all metrics
-        for idx ∈ indices_metrics
-            GC.gc()
+# make a map for a single collection 12-09 Dye_1
+varnames[indices_metrics[1]]
+varnames[indices_metrics[2]]
 
-            println("\t$(printnames[idx])")
+h2o_thresh = 0.25
+idx_mndwi = indices_metrics[1]
+idx = indices_metrics[1]
+# idx = argmin(abs.(λs .- 630.0))
 
-            # set up plot
-            size_in_inches = (4, 3)
-            dpi = 400
-            size_in_pixels = size_in_inches .* dpi
-            f = Figure(resolution=size_in_pixels)
-            ax = CairoMakie.Axis(f[1,1], xlabel="longitude", ylabel="latitude", title="$day")
-            heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img)
-            xlims!(ax, -97.7168, -97.7125)
-            ylims!(ax, 33.70075, 33.7035)
+# set up plot
+size_in_inches = (4, 3)
+dpi = 400
+size_in_pixels = size_in_inches .* dpi
[…]

### 2023-09-04 paper/paper.tex

@@
 % cleveref: load \crefname definitions after \begin{document}
-
 %=================================================================
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=10.5cm]{./assets/radiance.eps}
-    \caption{Radiance spectrum captured for single HSI pixel.}
-    \label{fig:radiance}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=10.5cm]{./assets/solar_irradiance.eps}
-    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
-    \label{fig:solar-irradiance}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=10.5cm]{./assets/reflectance_rainbow.eps}
-    \caption{Resuliting reflectance spectrum.}
-    \label{fig:reflectance}
-\end{figure}
-
 \subsection{Georectification Procedure}
@@
     \centering
-    \includegraphics[width=10.5cm]{./figures/demo-rectified-cube.png}
-    \caption{Georectified Hyperspectral Datacube}
-    \label{fig:rectified-cube}
+    \includegraphics[width=10.5cm]{./figures/annotated-hsi.eps}
+    \caption{Radiance spectrum captured for single HSI pixel.}
+    \label{fig:pipeline}
 \end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=10.5cm]{./figures/pipeline-figure.eps}
+    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
+    \label{fig:annotated-hsi}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Discussion}
+
+- Incorporation of drone into autonomous robotic team
+- Long range wireless network (ubiquiti) for data downlink
+- Incorporation of edge-ML for direct determination of chemical concentration
+- Utility for navigation, waste removal, etc...
+
+Discuss drawbacks (striping in images)
 

### 2023-09-05 1c_timing-tests.jl
updated timings

@@ -31,9 +31,11 @@ suite["reflectance-conversion"]["NoDye_1"] = @benchmarkable HyperspectralImage($
 suite["reflectance-conversion"]["Scotty_1"] = @benchmarkable HyperspectralImage($f3.bilpath, $f3.bilhdr, $f3.lcfpath, $f3.timespath, $f3.specpath, $f3.spechdr; isflipped=true)
 
 
-suite["resampling"]["Δx=0.05"] =  @benchmarkable resample_datacube_fast($hsi; Δx=0.05)
-suite["resampling"]["Δx=0.1"] =  @benchmarkable resample_datacube_fast($hsi; Δx=0.1)
-suite["resampling"]["Δx=0.25"] =  @benchmarkable resample_datacube_fast($hsi; Δx=0.25)
+suite["resampling"]["Δx=0.05"] = @benchmarkable resample_datacube_fast($hsi; Δx=0.05)
+suite["resampling"]["Δx=0.1"] = @benchmarkable resample_datacube_fast($hsi; Δx=0.1)
+suite["resampling"]["Δx=0.2"] = @benchmarkable resample_datacube_fast($hsi; Δx=0.2)
+suite["resampling"]["Δx=0.3"] = @benchmarkable resample_datacube_fast($hsi; Δx=0.3)
+suite["resampling"]["Δx=0.4"] = @benchmarkable resample_datacube_fast($hsi; Δx=0.4)
 suite["resampling"]["Δx=0.5"] =  @benchmarkable resample_datacube_fast($hsi; Δx=0.5)
 
 
@@ -41,7 +43,7 @@ tune!(suite);
 results = run(suite, verbose=true, seconds=100)
 
 
-
+println("Writing to file...")
 open("./paper/timing-results.txt", "w") do file
 
     println(file, "---")
@@ -75,9 +77,21 @@ open("./paper/timing-results.txt", "w") do file
     println(file, "\n")
 
     println(file, "---")
-    println(file, "Resampling results for Δx=0.25")
+    println(file, "Resampling results for Δx=0.4")
     println(file, "---")
-    println(file, mean(results["resampling"]["Δx=0.25"]))
+    println(file, mean(results["resampling"]["Δx=0.4"]))
+    println(file, "\n")
+
+    println(file, "---")
+    println(file, "Resampling results for Δx=0.3")
+    println(file, "---")
[…]

### 2023-09-08 1d_datacub_viz.jl
adding more smaple spectra

@@ -7,11 +7,11 @@ using MintsMakieRecipes
 set_theme!(mints_theme)
 
 my_theme = mints_theme
-my_theme.Axis.xticklabelsize=17
-my_theme.Axis.yticklabelsize=17
-my_theme.Axis.xlabelsize=20
-my_theme.Axis.ylabelsize=20
-my_theme.Axis.titlesize=22
+my_theme.Axis.xticklabelsize=20
+my_theme.Axis.yticklabelsize=20
+my_theme.Axis.xlabelsize=22
+my_theme.Axis.ylabelsize=22
+my_theme.Axis.titlesize=25
 set_theme!(my_theme)
 
 
@@ -47,6 +47,9 @@ varnames = read(h5["data-Δx_0.1/varnames"])
 printnames = read(h5["data-Δx_0.1/printnames"])
 λs = read(h5["data-Δx_0.1/λs"])
 
+rgb = getRGB(h5)
+
+close(h5)
 
 indices_metrics = findfirst(x-> x=="mNDWI", varnames):length(varnames)
 
@@ -59,7 +62,6 @@ fig = Figure(;resolution=size_in_pixels, figure_padding=50)
 ax = CairoMakie.Axis(fig[1,1], xlabel="Longitude", ylabel="Latitude")
 hm = heatmap!(ax, satmap.w..satmap.e, satmap.s..satmap.n, satmap.img)
 
-rgb = getRGB(h5)
 hm_rgb = heatmap!(ax, Longitudes, Latitudes, rgb)
 
 xlims!(ax, -97.717, -97.715)
@@ -71,7 +73,6 @@ save("./paper/figures/georectified-hsi-plume.png", fig)
 
 fig
 
-close(h5)
 
 # plot radiance, irradiance, and reflectance for single HSI (12-09 Dye_1-6) for a slice from the plume
 fpath = "/media/teamlary/LabData/RobotTeam/raw/hsi/12-09/Dye_1-6"
@@ -158,6 +159,7 @@ save("./paper/figures/reflectance-sample.svg", fig)
 save("./paper/figures/reflectance-sample.eps", fig)
 save("./paper/figures/reflectance-sample.pdf", fig)
 fig
+
 
 # plot single HSI on map (1209 Dye_1-6)
 varnames[indices_metrics[1]]

### 2023-09-08 1e_datacube-3d-vis.jl

@@ -7,6 +7,17 @@ using ProgressMeter
 using Statistics
 
 set_theme!(mints_theme)
+my_theme = mints_theme
+my_theme.Axis.xticklabelsize = 20
+my_theme.Axis.yticklabelsize = 20
+my_theme.Axis.xlabelsize = 22
+my_theme.Axis.ylabelsize = 22
+my_theme.Axis.titlesize = 25
+my_theme.Colorbar.ticklabelsize=20
+my_theme.Colorbar.labelsize=22
+set_theme!(my_theme)
+
+
 
 include("utils/vis_tools.jl")
 include("utils/config.jl")
@@ -25,17 +36,6 @@ fig, ax, hm = heatmap(img)
 size(img)
 
 
-
-my_theme = mints_theme
-my_theme.Axis.xticklabelsize=17
-my_theme.Axis.yticklabelsize=17
-my_theme.Axis.xlabelsize=20
-my_theme.Axis.ylabelsize=20
-my_theme.Axis.titlesize=22
-set_theme!(my_theme)
-
-
-
 # 1. create visualization of un-georectified HSI
 size_in_inches = (3, 3)
 dpi = 600
@@ -52,49 +52,152 @@ save("./paper/figures/demo-cube.png", fig)
 xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ = resample_datacube_fast(hsi; Δx=Δx)
 
 
+size_in_inches = (3, 3)
+dpi = 300
+size_in_pixels = size_in_inches .* dpi
+
+
+
 fig = vis_rectified_cube(Data_μ, xs, ys, IsInbounds, λs, Δx; offset=0.0, ibounds=(100, length(xs)), resolution=size_in_pixels, colorbar=true)
 
-colgap!(fig.layout, -300)
+colgap!(fig.layout, -100)
 
 fig
 
 save("./paper/figures/demo-rectified-cube.png", fig)
 
 
-ax = current_axis(fig)
-
-arrows!([(length(xs)-250)*Δx],[(length(ys))*Δx],[Δx*(-60)],[0],[0],[50*Δx]; arrowsize=1)
-
-
-save("./paper/figures/rectified-cube-w-arrow.png", fig)
-
-fig
 
 # plot reflectance of slice through the plume
 using CairoMakie
+
+set_theme!(figure_padding = 30)
 
 data = log10.(Data_μ[1:462,:,:])
[…]

### 2023-09-09 1d_datacub_viz.jl
updated theme settings and padding

@@ -6,19 +6,24 @@ using MintsMakieRecipes
 
 set_theme!(mints_theme)
 
-my_theme = mints_theme
-my_theme.Axis.xticklabelsize=20
-my_theme.Axis.yticklabelsize=20
-my_theme.Axis.xlabelsize=22
-my_theme.Axis.ylabelsize=22
-my_theme.Axis.titlesize=25
-set_theme!(my_theme)
+update_theme!(
+    figure_padding=30,
+    Axis = (
+        xticklabelsize=20,
+        yticklabelsize=20,
+        xlabelsize=22,
+        ylabelsize=22,
+        titlesize=25,
+    ),
+    Colorbar = (
+    ticklabelsize=20,
+    labelsize=22
+        )
+)
 
 
 include("utils/vis_tools.jl")
 include("utils/config.jl")
-
-
 
 
 basepath
@@ -135,6 +140,28 @@ save("./paper/figures/radiance-sample.png", fig)
 save("./paper/figures/radiance-sample.svg", fig)
 save("./paper/figures/radiance-sample.eps", fig)
 save("./paper/figures/radiance-sample.pdf", fig)
+
+
+
+fig = Figure();
+ax = CairoMakie.Axis(
+    fig[1, 1],
+    xlabel="λ (nm)",
+    ylabel="Downwelling Irradiance",
+    yticksvisible=false,
+    ygridvisible=false,
+    yminorgridvisible=false,
+    yticklabelsvisible=false,
+)
+ls = lines!(λs_irrad, irrad_dat, color=:orange, linewidth=3)
+xlims!(λs_irrad[1], λs_irrad[end])
+ylims!(0, nothing)
+fig
+
+save("./paper/figures/irradiance-smaple.png", fig)
+save("./paper/figures/irradiance-smaple.svg", fig)
+save("./paper/figures/irradiance-smaple.eps", fig)
+save("./paper/figures/irradiance-smaple.pdf", fig)
 
 
 λ_blue = 495.0

### 2023-09-09 1e_datacube-3d-vis.jl

@@ -6,17 +6,23 @@ using MintsMakieRecipes
 using ProgressMeter
 using Statistics
 
-set_theme!(mints_theme)
-my_theme = mints_theme
-my_theme.Axis.xticklabelsize = 20
-my_theme.Axis.yticklabelsize = 20
-my_theme.Axis.xlabelsize = 22
-my_theme.Axis.ylabelsize = 22
-my_theme.Axis.titlesize = 25
-my_theme.Colorbar.ticklabelsize=20
-my_theme.Colorbar.labelsize=22
-set_theme!(my_theme)
 
+set_theme!(mints_theme)
+
+update_theme!(
+    figure_padding=30,
+    Axis=(
+        xticklabelsize=20,
+        yticklabelsize=20,
+        xlabelsize=22,
+        ylabelsize=22,
+        titlesize=25,
+    ),
+    Colorbar=(
+        ticklabelsize=20,
+        labelsize=22
+    )
+)
 
 
 include("utils/vis_tools.jl")
@@ -71,7 +77,6 @@ save("./paper/figures/demo-rectified-cube.png", fig)
 # plot reflectance of slice through the plume
 using CairoMakie
 
-set_theme!(figure_padding = 30)
 
 data = log10.(Data_μ[1:462,:,:])
 idx_not_nan_or_inf = findall(.!(isnan.(data)) .&& .!(isinf.(data)))
@@ -119,6 +124,7 @@ leg = axislegend(
     position=:lt,
 )
 xlims!(λs[1], λs[end])
+ylims!(0, nothing)
 fig
 
 save("./paper/figures/reflectance-samples.png", fig)
@@ -132,6 +138,7 @@ fig2 = Figure();
 ax = CairoMakie.Axis(fig2[1, 1], xlabel="λ (nm)", ylabel="Reflectance");
 ls = lines!(ax, λs, Data_μ[1:462, idx_plume], color=data[1:462, idx_plume], colormap=:jet, colorrange=(Rmin, Rmax), linewidth=3.5)
 xlims!(λs[1], λs[end])
+ylims!(0, nothing)
 fig2
 
 save("./paper/figures/reflectance-plume.png", fig2)
@@ -145,6 +152,7 @@ fig2 = Figure();
 ax = CairoMakie.Axis(fig2[1, 1], xlabel="λ (nm)", ylabel="Reflectance");
[…]

### 2023-09-11 paper/paper.tex
Updates from Overleaf

@@
 
+\subsection{Drone Components}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=12cm]{./assets/annotated-drone.eps}
+    \caption{Components of the Autonomous Drone HSI platform.}
+    \label{fig:drone-components}
+\end{figure}
+
 \subsection{Reflectance Conversion}
@@
     \centering
-    \includegraphics[width=10.5cm]{./figures/annotated-hsi.eps}
-    \caption{Radiance spectrum captured for single HSI pixel.}
-    \label{fig:pipeline}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
     \includegraphics[width=10.5cm]{./figures/pipeline-figure.eps}
@@
 \section{Results}
+
+\begin{figure}[H]
+    \begin{adjustwidth}{-\extralength}{0cm}
+        \centering
+        \includegraphics[width=15.5cm]{./figures/hsi-infographic.eps}
+    \end{adjustwidth}
+    \caption{Annotated view of a hyperspectral data cube showcasing sampled spectra for a variety of constituents.\label{fig:hsi-infographic}}
+\end{figure}
 
@@
 \midrule
-0.5		&   1.328	\\
-0.25    &   1.547	\\
-0.1     &   3.557   \\
-0.05    &   9.235   \\
+0.5		&   1.434	\\
+0.4     &   1.545	\\
+0.3     &   1.673   \\
+0.2     &   1.802   \\
+0.1     &   4.026   \\
+0.05    &   10.537  \\ 
 \bottomrule
@@
     \midrule
-    371		&   2.049	\\
-    725    &   4.219	\\
-    1000     &   5.875   \\
+    371		&   2.060	\\
+    725     &   4.227	\\
+    1000    &   5.901   \\
     \bottomrule

### 2023-09-11 paper/paper.tex
Updates from Overleaf

@@
 \section{Introduction}
-Overview of Hyperspectral Imagery
 
-Multi-spectral vs Hyperspectral imagery
+- Global change necessitating better sensing technology 
+- Need to be able to track changes to water/plant/forest/land quality for better environmental management and disaster mitigation
+    - Palestine Ohio
+    - fires in Canada and Maui
+    - Oil Spill clean up
 
-Paragraph about previous uses of HSI technology in remote sensing applications. Plant health, NDVI, water applications, land management, etc...
+- multi-spectral and hyper-spectral imaging
+- in remote sensing
+    - discuss satellite remote sensing 
+    - multi-spectral platforms: MODIS, Sentinel, etc... 
+    - upcoming hyper-spectral platforms:
+- from Airplanes
+- Land change tracking (water erosion, deforestation, desertification )
+- Mention popular spectral indices like the NDVI
+
+- Paragraph about use of drones for remote sensing 
+    - smart agriculture
+    - photogrametry and DEMs (Open Drone Map)
+
+- Paragraph about the need of georectification 
+    - Georectification = georeference + orthorectification
+    - outline other papers that have discussed georectification techniques: 
+        - ground control points 
+        - IMU / GPS 
+        - different type of sensors: square, pushbroom, whiskbroom
+
+- Paragraph about difficulties of real time HSI application 
+    - data volume (storage, transfer/streaming)
+    - payload size 
+    - what we really want (usually) isn't the full spectra at each pixel 
+        - spectral indices (NDVI, etc.) 
+        - Chemical concentrations (chlorophyll, crude oil, etc...)
+
+- Paragraph about advances in hyper-spectral imaging technology, drones, and miniaturized computers (e.g. the raspberry pi, jetson nano, intel nuc, etc...)
+
+- finally, introduce the paper via the Robot team --> e.g. cite the paper and talk about how we're going to focus on the drone in detail in this paper.
 
@@
 
-Application: Our robotic team
-
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Materials and Methods}
-Overview of the HSI
 
-Overview of the Aerial Vehicle Platform (w/ NUC and SSD)
+\subsection{Autonomous Aerial Vehicle}
+
+subsection detailing the robot team, and specifically, the drone setup (HSI, NUC, Flir, etc...) 
+- HSI takes images 
+- IMU/GPS onboard position/orientation determination
+- Intel NUC 1: manages HSI
+- SSD
+- Intel NUC 2: Processing 
+- Ubiquity long-range wifi antenna (for streaming data products)
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=12cm]{./assets/annotated-drone.eps}
+    \caption{Components of the Autonomous Drone HSI platform.}
+    \label{fig:drone-components}
+\end{figure}
+
+\subsection{Real time processing of HSI imagery}
+
+- overview of processing pipeline
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=10.5cm]{./figures/pipeline-figure.eps}
+    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
+    \label{fig:annotated-hsi}
+\end{figure}
+
+- Collection of raw HSI by imager
+- Reading stored binary (ENVI) radiance data into tensor
+- Reading Flight Data 
+- Interpolate flight data from IMU to match HSI times
+- Reading stored downwelling irradiance spectrum 
+- Interpolate irradiance spectrum to match HSI $\lambda$s 
+- Conversion to Reflectance under the assumption of a Lambertian surface (perfectly diffuse)
+- Georectify to obtain new coordinates
+- resample to regular grid
+- compute derived $\lambda$-metrics (NDVI, etc...) 
+- serve result (save to HDF5 or serve via web map service over wifi)
 
@@
 
-\subsection{Drone Components}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=12cm]{./assets/annotated-drone.eps}
-    \caption{Components of the Autonomous Drone HSI platform.}
-    \label{fig:drone-components}
-\end{figure}
-
-\subsection{Reflectance Conversion}
-
-Here we can detail the conversion from radiance to reflectance using the downwelling irradiance spectrum with the assumption of a Lambertian surface.
-
-\textbf{NOTE:} we should update the following three figures to make a single figure with the radiances/irradiance in on the left (using the left and right y-axis) and the reflectance on the right.
-
 \subsection{Georectification Procedure}
@@
     \label{fig:georectification}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=10.5cm]{./figures/pipeline-figure.eps}
-    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
-    \label{fig:annotated-hsi}
 \end{figure}

### 2023-09-15 paper/paper.tex

@@
 % Full title of the paper (Capitalized)
-\Title{Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle}
+\Title{Rapid Georeferencing n of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle}
 
@@
 \abstract{Recent developments in hyperspectral imaging technology have led to dramatic reductions in both size and weight of imaging platforms.
-Due to these improvements, it is now possible to incorporate the technology as the payload of autonomous aerial vehicles such as drones.
+Due to these improvements, it is now possible to incorporate the technology as the payload of highly mobile autonomous aerial vehicles such as drones.
 However, the massive volume of hyperperspectral datacubes poses significant computational challenges to their adoption in real-time applications.
-In this paper, we develop a procedure for the rapid georectification of pushbroom imagery and demonstrate its application for real-time remote sensing...
+In this paper, we demonstrate a procedure for the rapid georeferencing of pushbroom imagery and demonstrate its application for real-time remote sensing...
 Results indicate that a typical image can be processed in ~10 seconds while it takes $x$ seconds to capture.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
-\section{How to Use this Template}
-
-The template details the sections that can be used in a manuscript.
-Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
-Please check the instructions on the authors' page of the journal to verify the correct order and names.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References).
-Only journal Laws uses \footnote.
-
-% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.
 
@@
 
-- Global change necessitating better sensing technology 
-- Need to be able to track changes to water/plant/forest/land quality for better environmental management and disaster mitigation
-    - Palestine Ohio
-    - fires in Canada and Maui
-    - Oil Spill clean up
+In this paper, we implement a procedure for rapid georeferencing of hyper-spectral imagery acquired by an autonomous aerial vehicle, and in doing so, demonstrate the feasibility of the platform for real time characterization of novel environments.
+
+In the face of rapidly accelerating global change, there is a demonstrated need for advanced remote sensing technologies. For decades
+
+\subsection{Hyperspectral Imaging}
 
@@
 
-- Paragraph about use of drones for remote sensing 
-    - smart agriculture
-    - photogrametry and DEMs (Open Drone Map)
+\subsection{Georeferencing}
 
@@
         - different type of sensors: square, pushbroom, whiskbroom
+
+\subsection{Drone based Platforms}
+
+- Paragraph about use of drones for remote sensing 
+    - smart agriculture
+    - photogrametry and DEMs (Open Drone Map)
+
+\subsection{Computational Difficulties}
 
@@
 
+- Challenges of using HSI in real-time applications: Data volume, processing power, data streaming.
+Data are much to big to be streamed to the ground in real time; for this application, imagery need to be collected, georeferenced, and then turned into data products \emph{onboard the drone} before they can be readily streamed to the ground.
+We can always re-process the imagery later for an in-depth reanalysis, but for time-critical applications, we need all of the processing to happen on board the drone.
+
 - finally, introduce the paper via the Robot team --> e.g. cite the paper and talk about how we're going to focus on the drone in detail in this paper.
 
-Challenges of using HSI in real-time applications: Data volume, processing power, data streaming.
-Data are much to big to be streamed to the ground in real time; for this application, imagery need to be collected, georeferenced, and then turned into data products \emph{onboard the drone} before they can be readily streamed to the ground.
-We can always re-process the imagery later for an in-depth reanalysis, but for time-critical applications, we need all of the processing to happen on board the drone.
+IMU - inertial measurement unit
+
+In the realm of remote sensing, the utilization of multi-spectral and hyper-spectral imaging technologies has ushered in a new era of unprecedented capabilities for Earth observation and environmental monitoring.
+Multi-spectral imaging, which captures data across a limited number of discrete spectral bands, and hyper-spectral imaging, which offers a significantly higher number of finely spaced spectral channels, have become invaluable tools for discerning intricate details of our planet's surface and atmosphere.
+These advanced imaging techniques enable researchers to detect and analyze subtle variations in the reflectance, absorption, and emission properties of materials across the electromagnetic spectrum.
+They have found applications in a myriad of fields, from agriculture and forestry to geology and environmental science, by enhancing our ability to discriminate between different land cover types, identify chemical compositions, and monitor changes in vegetation health and atmospheric constituents \cite{remote-sensing-foliage, crop-indices-2000}.
 

### 2023-09-16 src/ENVI/ENVI.jl
removed function we arent using and changes HSI definition to allow parametric types for data

@@ -14,7 +14,6 @@ export EnviHeaderParsingError
 export read_envi_header
 export get_envi_params
 export read_envi_file
-export envi_to_hdf5
 
 export FlightData, HyperspectralImage
 
@@ -281,161 +280,6 @@ end
 
 
 
-"""
-    envi_to_hdf5(fpath::String, hdrpath::String, lcfpath::outpath::String)
-
-Read ENVI formatted HSI file from `fpath` and its associated metadata file `hdrpath`. Save the array to an hdf5 file at `outapth`.
-"""
-function envi_to_hdf5(
-    bilpath::String,
-    bilhdr::String,
-    lcfpath::String,
-    timespath::String,
-    specpath::String,
-    spechdr::String,
-    outpath::String;
-    )
-
-    # assume year is 2019 and overwrite with year from hdr file
-    year = 2019
-
-    fid = h5open(outpath, "w")
-
-    println("\tcreating groups")
-    g = create_group(fid, "raw")
-
-    # create subgroups for each data set type
-    rad = create_group(g, "radiance")
-    down = create_group(g, "downwelling")
-    lcf = create_group(g, "lcf")
-    times = create_group(g, "times")
-
-    # use let block to keep img from persisting
-    let
-        println("\treading radiance")
-        img, h, p = read_envi_file(bilpath, bilhdr)
-
-        year = parse(Int, split(split(p["timestamp"], "-")[1], "/")[end])
-        println("\tyear taken: $(year)")
-
-        # write the envi radiance data
-        rad["radiance", chunk=(p["nbands"], 1, 1)] = img
-        # rad["wavelengths"] = parse.(Float64, h["wavelength"])
-        for (key, val) ∈ p
-            if key != "dtype"
-                rad[key] = val
-            end
-        end
-    end
-
-    let
-        println("\treading downwelling irradiance")
-        spec, hspec, pspec = read_envi_file(specpath, spechdr)
-        # write the downwelling irradiance
-        down["irradiance"] = spec
-        for (key, val) ∈ pspec
-            if key != "dtype"
-                down[key] = val
[…]

### 2023-09-16 src/RobotTeam.jl
removed old function export

@@ -9,7 +9,6 @@ export EnviHeaderParsingError
 export read_envi_header
 export get_envi_params
 export read_envi_file
-export envi_to_hdf5
 export FlightData, HyperspectralImage
 
 

### 2023-09-16 src/Georectification/georectify.jl
simplified coordinate generation

@@ -79,7 +79,6 @@ function generateCoords!(
         rs_pixel_sensor = [imagecoords(i,j,N,focal_length) for i∈1:3, j∈1:N]
     end
 
-
     # loop through and set viewing angle
     @tturbo for i ∈ 1:N, j∈1:lines
         ViewAngle[i,j] = atan(rs_pixel_sensor[2,i], rs_pixel_sensor[3,i])
@@ -97,11 +96,17 @@ function generateCoords!(
     isnorth = fdata.isnorth
     zone = fdata.zone
 
+    # define the coord transformation
+    lla_from_utm = LLAfromUTM(zone, isnorth, wgs84)
+
     # set up drone coordinates
     droneCoords = Array{Float64}(undef, 3, lines)
     @inbounds droneCoords[1,:] .= fdata.xs
     @inbounds droneCoords[2,:] .= fdata.ys
     @inbounds droneCoords[3,:] .= fdata.zs
+
+    s = 0.0
+    rs_object_utm = zeros(size(rs_pixel_sensor))
 
     Threads.@threads for line ∈ 1:lines
         # compute scale factor
@@ -123,32 +128,26 @@ function generateCoords!(
 
         # update pixel times
         Times[:,line] .= ts[line]
+    end
 
-        # convert back to latitude, longitude
-        for j ∈ 1:N
-            lla = LLAfromUTMZ(wgs84)(UTMZ(rs_object_utm[:,j]..., zone, isnorth))
-            @inbounds Latitudes[j,line] = lla.lat
-            @inbounds Longitudes[j,line] = lla.lon
+    X_utm = [UTM(X[1,i,j], X[2,i,j], X[3,i,j]) for i ∈ 1:N, j ∈ 1:lines]
+    X_lla = map(lla_from_utm, X_utm)
 
-            az,el = solar_azimuth_altitude(
-                Times[j,line],
+    Threads.@threads for i ∈ 1:N
+        for j ∈ 1:lines
+            @inbounds Latitudes[i,j] = (X_lla[i,j]).lat
+            @inbounds Longitudes[i,j] = (X_lla[i,j]).lon
+
+            SolarAzimuth[i,j],SolarElevation[i,j] = solar_azimuth_altitude(
+                Times[i,j],
                 start_time,
-                lla.lat,
-                lla.lon,
-                lla.alt
+                X_lla[i,j].lat,
+                X_lla[i, j].lon,
[…]

### 2023-09-16 src/ENVI/ENVI.jl
fixed type issue to allow for abstractarray subtypes

@@ -362,7 +362,7 @@ end
 
 
 
-struct HyperspectralImage{T0, T1}
+struct HyperspectralImage{T0, T1<:AbstractArray}
     # UTMz information
     X::Array{T0, 3}  # x,y,z
     zone::UInt8
@@ -380,7 +380,7 @@ struct HyperspectralImage{T0, T1}
     λs::Vector{T0}
 
     # Datacube
-    Datacube::Array{T1,3}
+    Datacube::T1
 
     # Viewing Geometry
     Roll::Matrix{T0}

### 2023-09-16 .dev-georectify.jl
removing _mu from Data

@@ -1,0 +1,141 @@
+using RobotTeam
+using BenchmarkTools
+using HDF5
+using CairoMakie
+using MintsMakieRecipes
+
+set_theme!(mints_theme)
+
+basepath = "/home/teamlary/gitrepos/utd/RobotTeam.jl/data/raw"
+
+# three HSI files to test
+f1 = get_raw_file_list(get_bil_files(basepath, "Dye_1")[1])
+f2 = get_raw_file_list(get_bil_files(basepath, "NoDye_1")[1])
+f3 = get_raw_file_list(get_bil_files(basepath, "Scotty_1")[1])
+
+
+
+@benchmark read_envi_header($f1.bilhdr)  # 107 μs
+
+h = read_envi_header(f1.bilhdr)
+
+@benchmark get_envi_params($h)  # 46 μs
+
+params = get_envi_params(h)
+
+
+# this reads in the relevant flight data time-stamped to the correct
+@benchmark FlightData($f1.lcfpath, $f1.timespath)  # 3.126 ms
+fd = FlightData(f1.lcfpath, f1.timespath)
+fd.start_time
+
+
+
+@benchmark read_envi_file($f1.bilpath, $f1.bilhdr)  # 337 ms
+@benchmark read_envi_file($f1.specpath, $f1.spechdr)  # 651.675 μs
+
+
+
+
+
+# 1. read the raw radiance cube
+
+Datacube, h, p = read_envi_file(f1.bilpath, f1.bilhdr)
+
+size(Datacube)
+
+X = zeros(3, size(Datacube,2), size(Datacube,3))
+Latitudes  = zeros(size(Datacube,2), size(Datacube,3))
+Longitudes = zeros(size(Datacube,2), size(Datacube,3))
+Roll = zeros(size(Datacube,2), size(Datacube,3))
+Pitch = zeros(size(Datacube,2), size(Datacube,3))
+Heading = zeros(size(Datacube,2), size(Datacube,3))
+Times = zeros(size(Datacube,2), size(Datacube,3))
+ViewAngle = zeros(size(Datacube,2), size(Datacube,3))
+SolarAzimuth = zeros(size(Datacube,2), size(Datacube,3))
+SolarElevation = zeros(size(Datacube,2), size(Datacube,3))
+SolarZenith = zeros(size(Datacube,2), size(Datacube,3))
+fd.start_time
+
+@benchmark generateCoords!(
+    X,
[…]

### 2023-09-16 src/Georectification/Georectification.jl

@@ -26,7 +26,6 @@ const offset_hdr = @path normpath(joinpath(@__DIR__, "../../assets", "calibratio
 
 include("reflectance.jl")
 export generateReflectance!
-export generateDerivedMetrics!
 
 include("georectify.jl")
 export generateCoords!
@@ -39,7 +38,7 @@ export build_mesh
 include("resample.jl")
 export bump_to_nearest_Δx, get_new_bounds, get_resampled_grid, resample_datacube, save_resampled_hsi
 export resample_datacube_fast, save_resampled_hsi_fast
-
+export generate_derived_metrics!
 
 
 include("folder_utils.jl")
@@ -50,9 +49,7 @@ function HyperspectralImage(
     bilpath::String,
     bilhdr::String,
     lcfpath::String,
-    timespath::String,
-    specpath::String,
-    spechdr::String;
+    timespath::String;
     θ_view=30.8,
     z_ground=292.0,
     isflipped=false
@@ -78,7 +75,6 @@ function HyperspectralImage(
     start_time = fdata.start_time
     λs = p["wavelengths"]
 
-    Reflectance = Array{Float64}(undef, nbands, nsamples, nscanlines)
 
     Roll = Matrix{Float64}(undef, nsamples, nscanlines);
     Pitch = Matrix{Float64}(undef, nsamples, nscanlines);
@@ -91,11 +87,17 @@ function HyperspectralImage(
     SolarZenith = Matrix{Float64}(undef, nsamples, nscanlines);
 
 
-    # 3. Compute Reflectance Data
-    let
-        Radiance, h, p = read_envi_file(bilpath, bilhdr)
-        generateReflectance!(Reflectance, Radiance, specpath, spechdr, λs)
-    end
+    # read in datacube data
+    Datacube, h, p = read_envi_file(bilpath, bilhdr)
+
+    # # 3. Compute Reflectance Data
+    # Datacube = Array{Float64}(undef, nbands, nsamples, nscanlines)
+    # let
+    #     Radiance, h, p = read_envi_file(bilpath, bilhdr)
+    #     generateReflectance!(Datacube, Radiance, specpath, spechdr, λs)
+    # end
+
+
 
     # 3. Generate Coordinates
     generateCoords!(X,Longitudes, Latitudes, Roll,Pitch,Heading,Times,ViewingAngle,SolarAzimuth,SolarElevation,SolarZenith,start_time,fdata;θ_view=θ_view,z_ground=z_ground,isflipped=isflipped)
[…]

### 2023-09-16 src/Georectification/reflectance.jl

@@ -40,6 +40,43 @@ function generateReflectance!(Reflectance, Radiance, specpath, spechdr, λs)
 end
 
 
+function generateReflectance!(Data, specpath, spechdr, λs)
+    # load in downwelling spectrum
+    spectrum, hspec, pspec = read_envi_file(specpath, spechdr);
+    spec = @view spectrum[:,1,1]
+
+    # load in correction data
+    gain, gain_h, gain_ps = read_envi_file(String(gain_path), String(gain_hdr));
+    offset, offset_h, offset_ps = read_envi_file(String(offset_path), String(offset_hdr));
+
+    # calculate shutter differences
+    cal_shutter = gain_ps["shutter"]
+    spec_shutter = pspec["shutter"]
+    gain_factor = cal_shutter/spec_shutter # should be a float
+
+    # produce correction frames
+    adjusted_gain = gain_factor .* gain[:,1,1]
+    frame = spec .- offset[:,1,1]
+
+    # calculate correction
+    correction = π .* adjusted_gain .* frame
+    clamp!(correction, 0, typemax(eltype(frame)))
+
+    # interpolate the correction to match the datacube's wavelengths
+    #----------------------------------------------------------------------
+    interp = CubicSpline(correction[:,1,1], pspec["wavelengths"])
+    adjustedSpec = interp.(λs)
+
+    # compute reflectance values, clamping them to be ∈ [0, 1]
+    @tturbo for λ ∈ axes(Data,1), i ∈ axes(Data,2), j ∈ axes(Data,3)
+        Data[λ, i, j] = clamp(π * Data[λ, i, j] / adjustedSpec[λ], 0.0, 1.0)
+    end
+end
+
+
+
+
+
 # function generateDerivedMetrics!(hsi::HyperspectralImage)
 #     println("generating derived spectral indices")
 

### 2023-09-16 src/Georectification/resample.jl

@@ -90,6 +90,110 @@ function get_resampled_grid(hsi::HyperspectralImage; Δx=0.1)
 end
 
 
+
+
+function resample_datacube_fast(hsi::HyperspectralImage; Δx=0.10)
+    # 1. resample to a square grid
+    println("\tgenerating new grid")
+    xs_new, ys_new, Xhsi_is, Xhsi_js, IsInbounds, ij_pixels, ij_notpixels, idx_dict = get_resampled_grid(hsi;Δx=Δx)
+
+    # 2. allocate latitudes and longitudes
+    Longitudes_out= Matrix{Float64}(undef, size(IsInbounds)...)
+    Latitudes_out = Matrix{Float64}(undef, size(IsInbounds)...)
+
+
+    lla_from_utm = LLAfromUTM(hsi.zone, hsi.isnorth, wgs84)
+
+    Threads.@threads for j ∈ axes(Longitudes_out,2)
+        for i ∈ axes(Longitudes_out,1)
+            lla = lla_from_utm(UTM(xs_new[i], ys_new[j], 0.0))
+
+            Longitudes_out[i, j] = lla.lon
+            Latitudes_out[i, j] = lla.lat
+        end
+    end
+
+
+    # 3. create vector of labels
+
+    varnames = [
+        ["R_"*lpad(idx, 3,"0") for idx ∈ 1:length(hsi.λs)]...,
+        "roll",
+        "pitch",
+        "heading",
+        "view_angle",
+        "solar_azimuth",
+        "solar_elevation",
+        "solar_zenith",
+    ]
+
+    printnames = [
+        ["Reflectance Band "*lpad(idx, 3,"0") for idx ∈ 1:length(hsi.λs)]...,
+        "Roll",
+        "Pitch",
+        "Heading",
+        "Viewing Angle",
+        "Solar Azimuth",
+        "Solar Elevation",
+        "Solar Zenith",
+    ]
+
+    # 4. Allocate Data Matrices
+    Data= Array{Float64}(undef, length(varnames), size(IsInbounds)...);
+
+    # set all out-of-bounds pixels to NaN
+    Data[:,ij_notpixels] .= NaN;
+
+    # 5. set up band indices
+    ks_reflectance = 1:length(hsi.λs)
+    k_roll = findfirst(varnames .== "roll")
[…]

### 2023-09-16 src/RobotTeam.jl

@@ -21,6 +21,7 @@ export generateCoords!
 export build_mesh
 export bump_to_nearest_Δx, get_new_bounds, get_resampled_grid, resample_datacube, save_resampled_hsi
 export resample_datacube_fast, save_resampled_hsi_fast
+export generate_derived_metrics!
 export get_bil_files, get_raw_file_list
 
 

### 2023-09-16 src/visualization.jl

@@ -75,9 +75,9 @@ function getRGB(h5::HDF5.File; λred=630.0, λgreen=532.0, λblue=465.0, Δx=0.1
     idx_g = argmin(abs.(λs .- λgreen))
     idx_b = argmin(abs.(λs .- λblue))
 
-    Rr = h5["data-Δx_$(Δx)/Data_μ"][idx_r, :, :]
-    Rg = h5["data-Δx_$(Δx)/Data_μ"][idx_g, :, :]
-    Rb = h5["data-Δx_$(Δx)/Data_μ"][idx_b, :, :]
+    Rr = h5["data-Δx_$(Δx)/Data"][idx_r, :, :]
+    Rg = h5["data-Δx_$(Δx)/Data"][idx_g, :, :]
+    Rb = h5["data-Δx_$(Δx)/Data"][idx_b, :, :]
 
     ij_pixels = findall(h5["data-Δx_$(Δx)/IsInbounds"][:,:])
     img = zeros(4, size(Rr)...)
@@ -221,16 +221,16 @@ end
 
 
 
-function vis_rectified_cube(Data_μ, xs, ys, IsInbounds, λs, Δx; ibounds=(1, 1), jbounds=(1, 1), offset = 0.1, colormap=:jet, resolution=(800, 600), azimuth=3π / 4, elevation=3π / 16, colorbar=false)
+function vis_rectified_cube(Data, xs, ys, IsInbounds, λs, Δx; ibounds=(1, 1), jbounds=(1, 1), offset = 0.1, colormap=:jet, resolution=(800, 600), azimuth=3π / 4, elevation=3π / 16, colorbar=false)
 
     nλs = length(λs)
 
     println("\tGenerating RGB view...")
     ij_pixels = findall(IsInbounds)
-    Ref_img = getRGB(Data_μ, λs, ij_pixels)
+    Ref_img = getRGB(Data, λs, ij_pixels)
 
     println("\tReshaping data for plotting...")
-    data = PermutedDimsArray(Data_μ[1:nλs, :, :], (2, 3, 1))
+    data = PermutedDimsArray(Data[1:nλs, :, :], (2, 3, 1))
 
     println("\tApplying log10...")
     data = log10.(data .+ offset)

### 2023-09-17 src/Georectification/resample.jl
fixed resampling issue in bump_to_nearest call that wasn't using proper delta x value

@@ -18,7 +18,7 @@ Given bounding box and a resolution `Δx`, expand bounding box to nearest Δx.
 """
 function get_new_bounds(xmin, xmax, ymin, ymax; Δx=0.1)
     Δx_cm = 100*Δx
-    @assert 100%Δx_cm == 0
+    # @assert 100%Δx_cm == 0
 
     # pad to nearest Δx
     xmin -= Δx
@@ -38,13 +38,15 @@ function get_resampled_grid(hsi::HyperspectralImage; Δx=0.1)
 
     bump_to_nearest_Δx(xmin, Δx)
 
+    println("ymin: ", ymin)
 
-    xmin, xmax, ymin, ymax = get_new_bounds(xmin, xmax, ymin, ymax)
+    xmin, xmax, ymin, ymax = get_new_bounds(xmin, xmax, ymin, ymax; Δx=Δx)
 
+    println("ymin bumped: ", ymin)
 
-    # estimate the bound for minimum pixel spacing in meters
-    npix = max(size(hsi.X)...)
-    Δx_min = min((ymax-ymin)/npix, (xmax-xmin)/npix)
+    # # estimate the bound for minimum pixel spacing in meters
+    # npix = max(size(hsi.X)...)
+    # Δx_min = min((ymax-ymin)/npix, (xmax-xmin)/npix)
 
 
     # generate a new x-y grid at the desired resolution
@@ -56,10 +58,13 @@ function get_resampled_grid(hsi::HyperspectralImage; Δx=0.1)
 
     Xhsi = bump_to_nearest_Δx.(hsi.X[1:2,:,:],Δx)
 
+    println("minimum x: ", minimum(Xhsi[1,:,:])-xmin)
+    println("minimum y: ", minimum(Xhsi[2,:,:])-ymin)
 
     # generate hsi pixel indices in outbound grid
     Xhsi_is = Matrix{Int}(undef, size(Xhsi, 2), size(Xhsi,3));
     Xhsi_js = Matrix{Int}(undef, size(Xhsi, 2), size(Xhsi,3));
+
     @tturbo for j ∈ axes(Xhsi, 3), i ∈ axes(Xhsi,2)
         Xhsi_is[i,j] = Int(round((Xhsi[1,i,j] - xmin)/Δx + 1))
         Xhsi_js[i,j] = Int(round((Xhsi[2,i,j] - ymin)/Δx + 1))
[…]

### 2023-09-17 src/Georectification/resample.jl
removed debug print statements

@@ -38,16 +38,7 @@ function get_resampled_grid(hsi::HyperspectralImage; Δx=0.1)
 
     bump_to_nearest_Δx(xmin, Δx)
 
-    println("ymin: ", ymin)
-
     xmin, xmax, ymin, ymax = get_new_bounds(xmin, xmax, ymin, ymax; Δx=Δx)
-
-    println("ymin bumped: ", ymin)
-
-    # # estimate the bound for minimum pixel spacing in meters
-    # npix = max(size(hsi.X)...)
-    # Δx_min = min((ymax-ymin)/npix, (xmax-xmin)/npix)
-
 
     # generate a new x-y grid at the desired resolution
     xs_new = round.(range(xmin, stop=xmax, step=Δx), digits=2)
@@ -57,9 +48,6 @@ function get_resampled_grid(hsi::HyperspectralImage; Δx=0.1)
     # Xout = permutedims(cat([x for x ∈ xs_new, y ∈ ys_new], [y for x ∈ xs_new, y ∈ ys_new], dims=3), (3,1,2))  # 1.7 ms
 
     Xhsi = bump_to_nearest_Δx.(hsi.X[1:2,:,:],Δx)
-
-    println("minimum x: ", minimum(Xhsi[1,:,:])-xmin)
-    println("minimum y: ", minimum(Xhsi[2,:,:])-ymin)
 
     # generate hsi pixel indices in outbound grid
     Xhsi_is = Matrix{Int}(undef, size(Xhsi, 2), size(Xhsi,3));

### 2023-09-18 1__georectify.jl
okay, got it working. I think it must have something to do with the SIMD in @tturbo

@@ -25,14 +25,18 @@ for (day, runs) ∈ CollectionsDict
                     f.bilhdr,
                     f.lcfpath,
                     f.timespath,
-                    f.specpath,
-                    f.spechdr;
                     isflipped=true
                 )
 
                 println("\tresampling to new grid")
-                xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data_μ, Data_σ = resample_datacube(hsi; Δx=Δx)
 
+                xs, ys, isnorth, zone, Longitudes, Latitudes, IsInbounds, varnames, printnames, λs, Data = resample_datacube(hsi)
+
+                println("\tconverting to reflectance")
+                generateReflectance!(Data, f.specpath, f.spechdr, λs)
+
+                println("\tgenerating derived metrics")
+                generate_derived_metrics!(Data, IsInbounds, varnames, λs)
 
                 fname = split(f.lcfpath, "/")[end-1] * ".h5"
 
@@ -48,8 +52,7 @@ for (day, runs) ∈ CollectionsDict
                     varnames,
                     printnames,
                     λs,
-                    Data_μ,
-                    Data_σ,
+                    Data,
                     joinpath(outpath, day, run, fname);
                     Δx=Δx,
                     is_spec_chunked=is_spec_chunked,

### 2023-09-18 1c_timing-tests.jl

@@ -6,145 +6,120 @@ using MintsMakieRecipes
 
 set_theme!(mints_theme)
 
+update_theme!(
+    figure_padding=30,
+    Axis=(
+        xticklabelsize=20,
+        yticklabelsize=20,
+        xlabelsize=22,
+        ylabelsize=22,
+        titlesize=25,
+    ),
+    Colorbar=(
+        ticklabelsize=20,
+        labelsize=22
+    )
+)
+
+
 include("utils/vis_tools.jl")
 include("utils/config.jl")
 
 
 basepath = "/home/teamlary/gitrepos/utd/RobotTeam.jl/data/raw"
-f1 = get_raw_file_list(get_bil_files(basepath, "Dye_1")[1])
-f2 = get_raw_file_list(get_bil_files(basepath, "NoDye_1")[1])
-f3 = get_raw_file_list(get_bil_files(basepath, "Scotty_1")[1])
+f1 = get_raw_file_list(get_bil_files(basepath, "NoDye_1")[1])
+f2 = get_raw_file_list(get_bil_files(basepath, "NoDye_1")[2])
+f3 = get_raw_file_list(get_bil_files(basepath, "NoDye_1")[3])
 
 f = f3
 
-
-hsi = HyperspectralImage(f.bilpath, f.bilhdr, f.lcfpath, f.timespath, f.specpath, f.spechdr; isflipped=true);
-
-
-suite = BenchmarkGroup()
-
-suite["reflectance-conversion"] = BenchmarkGroup()
-suite["resampling"] = BenchmarkGroup()
-
-suite["reflectance-conversion"]["Dye_1"] = @benchmarkable HyperspectralImage($f1.bilpath, $f1.bilhdr, $f1.lcfpath, $f1.timespath, $f1.specpath, $f1.spechdr; isflipped=true)
-suite["reflectance-conversion"]["NoDye_1"] = @benchmarkable HyperspectralImage($f2.bilpath, $f2.bilhdr, $f2.lcfpath, $f2.timespath, $f2.specpath, $f2.spechdr; isflipped=true)
-suite["reflectance-conversion"]["Scotty_1"] = @benchmarkable HyperspectralImage($f3.bilpath, $f3.bilhdr, $f3.lcfpath, $f3.timespath, $f3.specpath, $f3.spechdr; isflipped=true)
-
-
[…]

### 2023-09-18 src/Georectification/Georectification.jl

@@ -87,17 +87,8 @@ function HyperspectralImage(
     SolarZenith = Matrix{Float64}(undef, nsamples, nscanlines);
 
 
-    # read in datacube data
+    # read in datacube data and convert to Float64 representation
     Datacube, h, p = read_envi_file(bilpath, bilhdr)
-
-    # # 3. Compute Reflectance Data
-    # Datacube = Array{Float64}(undef, nbands, nsamples, nscanlines)
-    # let
-    #     Radiance, h, p = read_envi_file(bilpath, bilhdr)
-    #     generateReflectance!(Datacube, Radiance, specpath, spechdr, λs)
-    # end
-
-
 
     # 3. Generate Coordinates
     generateCoords!(X,Longitudes, Latitudes, Roll,Pitch,Heading,Times,ViewingAngle,SolarAzimuth,SolarElevation,SolarZenith,start_time,fdata;θ_view=θ_view,z_ground=z_ground,isflipped=isflipped)

### 2023-09-18 src/Georectification/reflectance.jl

@@ -68,426 +68,10 @@ function generateReflectance!(Data, specpath, spechdr, λs)
     adjustedSpec = interp.(λs)
 
     # compute reflectance values, clamping them to be ∈ [0, 1]
-    @tturbo for λ ∈ axes(Data,1), i ∈ axes(Data,2), j ∈ axes(Data,3)
+    @tturbo for j ∈ axes(Data,3), i ∈ axes(Data,2), λ ∈ axes(Data,1)
         Data[λ, i, j] = clamp(π * Data[λ, i, j] / adjustedSpec[λ], 0.0, 1.0)
     end
 end
-
-
-
-
-
-# function generateDerivedMetrics!(hsi::HyperspectralImage)
-#     println("generating derived spectral indices")
-
-#     R = @view hsi.Reflectance[:,:,:];
-#     λs = @view hsi.λs[:];
-
-#     # mNDWI
-#     kgreen = findfirst(λs .> 550)
-#     kswir = findfirst(λs .> 770)
-#     let
-#         mNDWI = -1 .* ones(size(R,2), size(R,3))
-
-#         green = @view R[kgreen,:,:]
-#         swir = @view R[kswir,:,:]
-
-#         numer = (green .- swir)
-#         denom = (green .+ swir)
-
-#         mNDWI[denom .> 0] = (numer ./ denom)[denom .> 0]
-
-#         println("\tsaving mNDWI")
-#         metrics["mNDWI"] = mNDWI
-#     end
-
-
-#     # NDVI "normalized difference vegetative index ∈ [-1, 1]"
-#     kir = findfirst(λs .> 800)
-#     kred = findfirst(λs .> 680)
-#     let
-#         NDVI = -2 .* ones(size(R,2), size(R,3))
-
-#         ir_band = @view R[kir,:,:]
-#         red_band = @view R[kred,:,:]
-
-#         numer = (ir_band .- red_band)
-#         denom = (ir_band .+ red_band)
-
-#         NDVI[denom .> 0] .= (numer ./ denom)[denom .> 0]
-
-#         println("\tsaving NDVI")
-#         metrics["NDVI"] = NDVI
-#     end
-
-
-#     # SR "simple ratio ∈ [0, 30]"
-#     let
-#         SR = -1 .* ones(size(R,2), size(R,3))
-
-#         ir_band = @view R[kir,:,:]
-#         red_band = @view R[kred,:,:]
[…]

### 2023-09-18 src/Georectification/resample.jl

@@ -1,6 +1,8 @@
 using Statistics
 using HDF5
 using Measurements
+
+
 """
     bump_to_nearest_Δx(val, Δx)
 
@@ -17,7 +19,7 @@ end
 Given bounding box and a resolution `Δx`, expand bounding box to nearest Δx.
 """
 function get_new_bounds(xmin, xmax, ymin, ymax; Δx=0.1)
-    Δx_cm = 100*Δx
+    # Δx_cm = 100*Δx
     # @assert 100%Δx_cm == 0
 
     # pad to nearest Δx
@@ -148,14 +150,16 @@ function resample_datacube_fast(hsi::HyperspectralImage; Δx=0.10)
     k_el = findfirst(varnames .== "solar_elevation")
     k_zen = findfirst(varnames .== "solar_zenith")
 
-
+    # convert Datacube to float first
+    Datacube = Float64.(hsi.Datacube)
     # 6. Resample the data
     println("\tinterpolating...")
     Threads.@threads for k ∈ 1:length(ij_pixels)
         @inbounds ij = ij_pixels[k]
 
         # copy reflectance
-        @inbounds Data[ks_reflectance, ij] = mean(hsi.Datacube[:, idx_dict[ij]], dims=2)[:, 1]
+        # @inbounds Data[ks_reflectance, ij] = mean(hsi.Datacube[:, idx_dict[ij]], dims=2)
+        @inbounds Data[ks_reflectance, ij] = mean(Datacube[:, idx_dict[ij]], dims=2)
 
         # copy Roll
         @inbounds Data[k_roll, ij] = mean(hsi.Roll[idx_dict[ij]])

### 2023-09-18 1c_timing-tests.jl
no longer using tturbo

@@ -33,6 +33,7 @@ f3 = get_raw_file_list(get_bil_files(basepath, "NoDye_1")[3])
 
 f = f3
 
+
 sizes = [5, 10, 15, 20, 25, 30, 35, 40, 45, 50]
 scanlines = [
     parse(Int, read_envi_header(f1.bilhdr)["lines"]),
@@ -132,6 +133,9 @@ size_in_inches = (5, 3)
 dpi = 300
 size_in_pixels = size_in_inches .* dpi
 
+scanlines
+reflectance_timings
+
 fig = Figure(resolution=size_in_pixels);
 ax1 = CairoMakie.Axis(fig[1,1], xlabel="number of scanlines", ylabel="Execution Time (seconds)", title="Loading and Georeferencing")
 ax2 = CairoMakie.Axis(fig[1,2], xlabel="number of scanlines", ylabel="Execution Time (seconds)", title="Radiance to Reflectance Conversion", yaxisposition=:right)
@@ -146,7 +150,7 @@ fig
 
 
 save("paper/figures/reflectance-timing.png", fig)
-save("paper/figures/reflectance-timing.pdf", fig)
+save("paper/figures/reflectance-timing.pdf", fig
 save("paper/figures/reflectance-timing.eps", fig)
 save("paper/figures/reflectance-timing.svg", fig)
 

### 2023-09-18 src/Georectification/reflectance.jl

@@ -68,9 +68,18 @@ function generateReflectance!(Data, specpath, spechdr, λs)
     adjustedSpec = interp.(λs)
 
     # compute reflectance values, clamping them to be ∈ [0, 1]
-    @tturbo for j ∈ axes(Data,3), i ∈ axes(Data,2), λ ∈ axes(Data,1)
-        Data[λ, i, j] = clamp(π * Data[λ, i, j] / adjustedSpec[λ], 0.0, 1.0)
+    # @tturbo for j ∈ axes(Data,3), i ∈ axes(Data,2), λ ∈ 1:length(λs)
+    #     Data[λ, i, j] = clamp(π * Data[λ, i, j] / adjustedSpec[λ], 0.0, 1.0)
+    # end
+
+    Threads.@threads for j ∈ axes(Data,3)
+        for i ∈ axes(Data,2)
+            for λ ∈ 1:length(λs)
+                Data[λ, i, j] = clamp(π * Data[λ, i, j] / adjustedSpec[λ], 0.0, 1.0)
+            end
+        end
     end
+
 end
 
 

### 2023-09-22 paper/draft.qmd
started quarto document

--- 2023-09-15 paper/paper.tex
@@
-%  LaTeX support: latex@mdpi.com 
-%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
+---
+title: "A Procedure for the Rapid Processing and Georeferencing of Hyperspectral Imagery for Real-Time use by an Autonomous Aerial Vehicle"
+date: today
+author: "John Waczak"
+format:
+    pdf: default
+reference-location: margin
+citation-location: margin
+bibliography: references.bib
+---
 
-%=================================================================
-\documentclass[remotesensing,article,submit,pdftex,moreauthors]{Definitions/mdpi}
+# Abstract
 
-%--------------------
-% Class Options:
-%--------------------
-%----------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
-% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
-
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
-% supfile = supplementary materials
-
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.
-
-%=================================================================
-% MDPI internal commands - do not modify
-\firstpage{1} 
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother
-\pubvolume{1}
-\issuenum{1}
-\articlenumber{0}
-\pubyear{2023}
-\copyrightyear{2023}
-%\externaleditor{Academic Editor: Firstname Lastname}
-\datereceived{ } 
-\daterevised{ } % Comment out if no revised date
-\dateaccepted{ } 
-\datepublished{ } 
-%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
-%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
-\hreflink{https://doi.org/} % If needed use \linebreak
-%\doinum{}
-%\pdfoutput=1 % Uncommented for upload to arXiv.org
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
-% cleveref: load \crefname definitions after \begin{document}
-%=================================================================
-% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
-
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{Rapid Georeferencing n of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle}
-
-% MDPI internal command: Title for citation in the left column
-\TitleCitation{Title}
-
-% Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
-
-% Authors, for the paper (add full first names)
-\Author{John Waczak $^{1,\dagger,\ddagger}$\orcidA{}, David Lary $^{2,\ddagger}$ and Firstname Lastname $^{2,}$*}
-
-%\longauthorlist{yes}
-
-% MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{John Waczak, David Lary and Firstname Lastname}
-
-% MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Waczak, J.; Lary, D.; Lastname, F.}
-% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
-$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
-
-% Contact information of the corresponding author
-\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
-
-% Current address and/or shared authorship
-\firstnote{Current address: Affiliation 3.} 
-\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-% Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Recent developments in hyperspectral imaging technology have led to dramatic reductions in both size and weight of imaging platforms.
+Recent developments in hyperspectral imaging technology have led to dramatic reductions in both size and weight of imaging platforms.
 Due to these improvements, it is now possible to incorporate the technology as the payload of highly mobile autonomous aerial vehicles such as drones.
@@
 Results indicate that a typical image can be processed in ~10 seconds while it takes $x$ seconds to capture.
-}
 
-% Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
+# Introduction
 
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
+For decades, *multi-spectral imagers* have seen wide spread adoption in the remote sensing community as a means to take advantage of the wealth of information contained in the reflectance spectra of materials.
+In addition to the three color filters of traditional cameras, *multi-spectral* imagers, like those deployed on MODIS, Sentinel 2, and other satellite missions, capture many additional features by utilizing wavelength bands ranging from the near-UV, through the visible spectrum, and into the Infrared.
+With this additional information, multi-spectral remote sensing platforms are able to aid in a variety of domains from tracking land change, characterizing deforestation, monitoring erosion, evaluating crop health, and many others (add references here).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Diversity
-%\LSID{\url{http://}}
+(**add a figure showing the different wavelength bands of publically available satellites**)
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Applied Sciences
-%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+These uses are justified by the reflectance features of materials across the electromagnetic spectrum; water has vibrational modes in the IR, pigments have absorption peaks in the visible, etc...(discuss the particular features present in different regions of the reflectance spectrum).
+Many currently used spectral indices like the *normalized difference vegatation index* (NDVI) take advantage of these spectral regions by comparing ratios of pigment sensitive passbands to the constant signals infrared to infer the abundance of chlorophyll, and consequently, the health of plants, to identify forest canopy, etc..(**add citations and expand**)
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data
-%\dataset{DOI number or link to the deposited data set if the data set is published separately.
-If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors.
-In this case, please submit the data set as a supplement.}
-%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
+However, despite the plethora of successful applications of multi-spectral imaging, more can be accomplished with the additional information provided by fully resolved spectra.
+For example, in the laboratory, spectrophotometry allows the direct determination of the concentrations of chemicals constituents in solution (**add more detail and references**) by deconvolution of a sample spetrum against libraries carefully collected of reference spectra: individual chemicals be uniquely identified by the characterstic location and shape of their absorption features.
+We should mention something about algal blooms-- harmful species display shifted reflectance peaks that can be used to identify toxic species.
+This information is effectively filtered away by the broad passbands of existing (find the spectra used in that book that show the different species of algae).
+To that end, *hyperspectral imagers* (HSI), which sample hundreds of wavelength binds at each pixel, have become the natural next step for remote sensing platforms with many planned to deployed in the coming years (**add references about soon-to-be-deployed HSI satellites**).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Toxins
-%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
+At the terrestrial level, drones (commonly, quadcoptrs, octocopters, and other similar multi-rotor craft) equipped with cameras are able to utlize techniques of photogrametry together with continuously sampled imagery to produce high quality digital elevation maps, high quality mosaics, 3-dimensional reconstructions, etc...
+These capabilities provide significant aid for structural analysis, smart agriculture, etc...
+Today, kilogram-scale HSI can be comfortably mounted to the payload of film-scale drones such as the AltaX and advancements in spectral sensing such as (**reference Ethan Minot's recent paper**) suggest that sizes of HSI will continue to shrink further expanding their application in this domain.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Encyclopedia
-%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}
+In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI  [@robot-team-1].
+In this paper, we present a procedure based on the method of [@muller-georeferencing] for the rapid processing and georeferencing of imagery captured by a pushbroom HSI mounted on an autonomous.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Advances in Respiratory Medicine
-%\addhighlights{yes}
-%\renewcommand{\addhighlights}{%
-
-%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
-Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it.
-Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
-%\textbf{What are the main findings?}
-% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
-% \item First bullet.
-% \item Second bullet.
-% \end{itemize}\vspace{3pt}
-%\textbf{What is the implication of the main finding?}
-% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
-% \item First bullet.
-% \item Second bullet.
-% \end{itemize}
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-In this paper, we implement a procedure for rapid georeferencing of hyper-spectral imagery acquired by an autonomous aerial vehicle, and in doing so, demonstrate the feasibility of the platform for real time characterization of novel environments.
+In this paper we implement a procedure for the rapid georeferencing of pushbroom hyper-spectral imagery acquired by an autonomous aerial vehicle, and in doing so, demonstrate the feasibility of the platform for real-time characterization of novel environments.
 
@@
 
-\subsection{Hyperspectral Imaging}
+## Georeferencing of Remote Sensing Imagery
+
+- Paragraph about the need of georectification 
+    - Georectification = georeference + orthorectification
+    - outline other papers that have discussed georectification techniques: 
+        - ground control points 
+        - IMU / GPS 
+        - different type of sensors: square, pushbroom, whiskbroom
+
+## Hyperspectral Imaging
 
@@
 
-\subsection{Georeferencing}
+## Towards Real-time Applications
 
-- Paragraph about the need of georectification 
-    - Georectification = georeference + orthorectification
-    - outline other papers that have discussed georectification techniques: 
-        - ground control points 
-        - IMU / GPS 
-        - different type of sensors: square, pushbroom, whiskbroom
+This is where we can discuss chief technical difficulties for the use of Hyperspectral Imaging in real-time applications and the need for georeferencing.
 
-\subsection{Drone based Platforms}
+## Drone Based Platforms
 
@@
     - photogrametry and DEMs (Open Drone Map)
-
-\subsection{Computational Difficulties}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
+# Materials and Methods
 
-\subsection{Autonomous Aerial Vehicle}
+## An HSI Equipped Autonomous Aerial Vehicle
 
-subsection detailing the robot team, and specifically, the drone setup (HSI, NUC, Flir, etc...) 
-- HSI takes images 
-- IMU/GPS onboard position/orientation determination
-- Intel NUC 1: manages HSI
-- SSD
-- Intel NUC 2: Processing 
-- Ubiquity long-range wifi antenna (for streaming data products)
+# Results
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=12cm]{./assets/annotated-drone.eps}
-    \caption{Components of the Autonomous Drone HSI platform.}
-    \label{fig:drone-components}
-\end{figure}
+# Discusion
 
-\subsection{Real time processing of HSI imagery}
-
-- overview of processing pipeline
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=10.5cm]{./figures/pipeline-figure.eps}
-    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
-    \label{fig:annotated-hsi}
-\end{figure}
-
-- Collection of raw HSI by imager
-- Reading stored binary (ENVI) radiance data into tensor
-- Reading Flight Data 
-- Interpolate flight data from IMU to match HSI times
-- Reading stored downwelling irradiance spectrum 
-- Interpolate irradiance spectrum to match HSI $\lambda$s 
-- Conversion to Reflectance under the assumption of a Lambertian surface (perfectly diffuse)
-- Georectify to obtain new coordinates
-- resample to regular grid
-- compute derived $\lambda$-metrics (NDVI, etc...) 
-- serve result (save to HDF5 or serve via web map service over wifi)
-
-Georectification Procedure.
-\begin{itemize}
-    \item collect datacube 
-    \item read HSI in ENVI format
-    \item read Flight Data 
-    \item interpolate flight data to HSI times 
-    \item read Downwelling irradiance spectrum
-    \item convert radiance to reflectance 
-    \item georectify to obtain new coordinates 
-    \item resample to regular grid
-    \item save results to HDF5
-\end{itemize}
-
-Code and data availability via OSN and Github
-
-\subsection{Georectification Procedure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=10.5cm]{./assets/georectification.eps}
-    \caption{Visual representation of scan-line geometry for the drone based hyperspectral imaging platform.}
-    \label{fig:georectification}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-
-\begin{figure}[H]
-    \begin{adjustwidth}{-\extralength}{0cm}
-        \centering
-        \includegraphics[width=15.5cm]{./figures/hsi-infographic.eps}
-    \end{adjustwidth}
-    \caption{Annotated view of a hyperspectral data cube showcasing sampled spectra for a variety of constituents.\label{fig:hsi-infographic}}
-\end{figure}
-
-\begin{figure}[H]
-    \includegraphics[width=10.5 cm]{./figures/regrid-timing.eps}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig-regridding-timing}}
-\end{figure}
-
-\begin{figure}[H]
-  \includegraphics[width=10.5 cm]{./figures/reflectance-timing.eps}
-  \caption{Description \label{fig-reflectance-timing}}
-\end{figure}
-
-NOTE: we need to update these timings by first copying the HSI to the local drive (off of the external hard drive). This will probably have some effect on the read/write speeds for the test.
-
-\begin{table}[H]
-\caption{Resampling times as a function of pixel resolution.\label{tab1}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CC}
-\toprule
-\textbf{Resolution (m)}	& \textbf{Execution time (s)}\\
-\midrule
-0.5		&   1.434	\\
-0.4     &   1.545	\\
-0.3     &   1.673   \\
-0.2     &   1.802   \\
-0.1     &   4.026   \\
-0.05    &   10.537  \\ 
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\begin{table}[H]
-  \caption{Loading and Reflectance Conversion Times.\label{tab1}}
-  \newcolumntype{C}{>{\centering\arraybackslash}X}
-  \begin{tabularx}{\textwidth}{CC}
-    \toprule
-    \textbf{Number of scan lines}	& \textbf{Execution time (s)}\\
-    \midrule
-    371		&   2.060	\\
-    725     &   4.227	\\
-    1000    &   5.901   \\
-    \bottomrule
-  \end{tabularx}
-\end{table}
-
-\textbf{NOTE} Stuff to do in this section:
-\begin{itemize}
-    \item  Create table with processing timings for each step on a typical HSI
-    \item Create second table comparing time for full processing including resampling to a variety of scales (e.g.
-5 cm, 10 cm, 25 cm) We will want a version of the processing function that does not include the uncertainties and the spectral indices
-    \item create pipeline visualization showing size of each of the data products and their step in the pipeline (ending with a dataproduct like the NDVI)
-    \item Create a figure showing the georeferenced image on top of the satellite background 
-    \item Create another figure of the entire map with a spectral index applied to one of the dye-release datasets (to demonstrate use for real-time application like oil-spill)
-    \item create a figure of a sample HSI datacube in 3-d like from the previous paper with the rgb image on the top. 
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-- Incorporation of drone into autonomous robotic team
-- Long range wireless network (ubiquiti) for data downlink
-- Incorporation of edge-ML for direct determination of chemical concentration
-- Utility for navigation, waste removal, etc...
-
-Discuss drawbacks (striping in images)
-
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
-
-% Only for the journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
-A supporting video article is available at doi: link.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
-
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
-
-\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
-You might choose to exclude this statement if the study did not require ethical approval.
-Please note that the Editorial Office might ask you for further information.
-Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans.
-OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals.
-OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}
-
-\informedconsent{Any research article describing a study involving humans should contain this statement.
-Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
-You might also choose to exclude this statement if the study did not involve humans.
-
-Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
-Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
-
-\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data.
-In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
-Where no new data were created, or where data is unavailable due to privacy or ethical re-strictions, a statement is still required.
-Suggested Data Availability Statements are available in section “MDPI Research Data Policies” at \url{https://www.mdpi.com/ethics}.}
-
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
-
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the~results''.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\sampleavailability{Samples of the compounds ... are available from the authors.}
-
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-
-\abbreviations{Abbreviations}{
-The following abbreviations are used in this manuscript:\\
-
-\noindent 
-\begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & Linear dichroism
-\end{tabular}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixstart
-\appendix
-\section[\appendixname~\thesection]{}
-\subsection[\appendixname~\thesubsection]{}
-The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-\begin{table}[H] 
-\caption{This is a table caption.\label{tab5}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\section[\appendixname~\thesection]{}
-All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{adjustwidth}{-\extralength}{0cm}
-%\printendnotes[custom] % Un-comment to print a list of endnotes
-
-\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-%\bibliography{your_external_BibTeX_file}
-
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-\begin{thebibliography}{999}
-% Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-\bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 3
-\bibitem[Author3(year)]{ref-book2}
-Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-% Reference 4
-\bibitem[Author4(year)]{ref-unpublish}
-Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-% Reference 5
-\bibitem[Author5(year)]{ref-communication}
-Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-% Reference 6
-\bibitem[Author6(year)]{ref-proceeding}
-Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-% Reference 7
-\bibitem[Author7(year)]{ref-thesis}
-Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-% Reference 8
-\bibitem[Author8(year)]{ref-url}
-Title of Site. Available online: URL (accessed on Day Month Year).
-\end{thebibliography}
-
-% If authors have biography, please use the format below
-%\section*{Short Biography of Authors}
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
-%{\textbf{Firstname Lastname} Biography of first author}
-%
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
-%{\textbf{Firstname Lastname} Biography of second author}
-
-% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\PublishersNote{}
-\end{adjustwidth}
-\end{document}
+# Conclusion

### 2023-09-22 paper/draft.qmd
updated introduction

@@
 
-In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI  [@robot-team-1].
-In this paper, we present a procedure based on the method of [@muller-georeferencing] for the rapid processing and georeferencing of imagery captured by a pushbroom HSI mounted on an autonomous.
+We should now make the argument about the need for improved methods for processing of HSI due the their dramatically larger size, i.e.
+the standard workflow of collecting imagery and then post processing (re: Open Drone Map) is a fantastic and well tested solution but prevents the use in time-critical applications.
+We can also reference the continued improvements to single-board computers such as the raspberry pi 4b (8 Gb of Ram), Jetson family (GPU equipped), and intel nuc (powerful work horses with miniscule form factors).
+To make real-time possible we need two things:
+1. Conversion from raw data (digital counts) to physical units like Reflectance 
+2. Georeferencing of captured imagery so features can be quickly geolocated
 
-In this paper we implement a procedure for the rapid georeferencing of pushbroom hyper-spectral imagery acquired by an autonomous aerial vehicle, and in doing so, demonstrate the feasibility of the platform for real-time characterization of novel environments.
+We can always re-process the imagery later for an in-depth reanalysis, but for time-critical applications, we need all of the processing to happen on board the drone.
 
-In the face of rapidly accelerating global change, there is a demonstrated need for advanced remote sensing technologies. For decades
-
-## Georeferencing of Remote Sensing Imagery
-
-- Paragraph about the need of georectification 
+Add a paragraph about georeferencing in particular:
 - Georectification = georeference + orthorectification
 - outline other papers that have discussed georectification techniques:
-        - ground control points 
+    - ground control points  (not reasonable for dangerous or water-based environments)
     - IMU / GPS
@@
 
-## Hyperspectral Imaging
+Discuss configurations of imagers and the development of georeferencing strategies, e.g.
+starting with the Muller paper and going to today.
+Mention potential for the incorporation of digital elevation maps together enabled by GPUs and video game engines (**reference that one paper that suggests using Unity or something similar for the projective geometry optimized for Cuda on NVIDIA GPUs**).
 
-- multi-spectral and hyper-spectral imaging
-- in remote sensing
-    - discuss satellite remote sensing 
-    - multi-spectral platforms: MODIS, Sentinel, etc... 
-    - upcoming hyper-spectral platforms:
-- from Airplanes
-- Land change tracking (water erosion, deforestation, desertification )
-- Mention popular spectral indices like the NDVI
+In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI  [@robot-team-1].
+In this paper, we present a procedure based on the method of [@muller-georeferencing] for the rapid processing and georeferencing of imagery captured by a pushbroom HSI mounted on an autonomous.
+Associated code can be freely accessed and downloaded in (**add reference to our repository**)
 
-## Towards Real-time Applications
-
-This is where we can discuss chief technical difficulties for the use of Hyperspectral Imaging in real-time applications and the need for georeferencing.
-
-## Drone Based Platforms
-
-- Paragraph about use of drones for remote sensing 
-    - smart agriculture
-    - photogrametry and DEMs (Open Drone Map)
-
-- Paragraph about difficulties of real time HSI application 
-    - data volume (storage, transfer/streaming)
-    - payload size 
-    - what we really want (usually) isn't the full spectra at each pixel 
-        - spectral indices (NDVI, etc.) 
-        - Chemical concentrations (chlorophyll, crude oil, etc...)
-
-- Paragraph about advances in hyper-spectral imaging technology, drones, and miniaturized computers (e.g. the raspberry pi, jetson nano, intel nuc, etc...)
-
-- Challenges of using HSI in real-time applications: Data volume, processing power, data streaming.
-Data are much to big to be streamed to the ground in real time; for this application, imagery need to be collected, georeferenced, and then turned into data products \emph{onboard the drone} before they can be readily streamed to the ground.
-We can always re-process the imagery later for an in-depth reanalysis, but for time-critical applications, we need all of the processing to happen on board the drone.
-
-- finally, introduce the paper via the Robot team --> e.g. cite the paper and talk about how we're going to focus on the drone in detail in this paper.
+(**This point can be saved for the supervised learning paper**) what we really want (usually) isn't the full spectra at each pixel
 
 IMU - inertial measurement unit
-
-In the realm of remote sensing, the utilization of multi-spectral and hyper-spectral imaging technologies has ushered in a new era of unprecedented capabilities for Earth observation and environmental monitoring.
-Multi-spectral imaging, which captures data across a limited number of discrete spectral bands, and hyper-spectral imaging, which offers a significantly higher number of finely spaced spectral channels, have become invaluable tools for discerning intricate details of our planet's surface and atmosphere.
-These advanced imaging techniques enable researchers to detect and analyze subtle variations in the reflectance, absorption, and emission properties of materials across the electromagnetic spectrum.
-They have found applications in a myriad of fields, from agriculture and forestry to geology and environmental science, by enhancing our ability to discriminate between different land cover types, identify chemical compositions, and monitor changes in vegetation health and atmospheric constituents \cite{remote-sensing-foliage, crop-indices-2000}.
 

### 2023-09-22 paper/draft.qmd
more updates

@@
 
+The increased spectral resolution of HSI systems poses unique challenges to their adoption for real time applications primarily stemming from the considerable size of generated data files.
+Current data collection workflows see researchers first perform the aerial survey (data collection) and then transfer data to ground based computers for post processing.
+This workflow is well established in the remote sensing community where, as an example, compressed raw imagery from Sentinel-2 are transferred to the ground and then subsequently post processed into their final L1C (top of atmosphere) and L2A (bottom of atmosphere) data products ((**add citation here**)).
+Drone based applications often operate in a similar manner: images or video are collected by a survey and then post-processed and analyzed with software such as Open Drone Map to produce the desired data products (tile mosaics, 3d reconstructions, etc.) (**add citation**).
+For an HSI platform to function in real time, three key computational tasks are critical:
+1. **FileIO**: captured imagery need to be quickly read by the on-board processing computer
+2.
+**Post-processing**: Raw imagery need to be rapidly converted to the chosen data product (typically, Reflectance), and importantly, must be georeferenced so that each image pixel can be located on the ground.
+3. **Ground Transfer**: Sufficient wireless communication must be avaiable to transmit the final
+
+The first can be readily accomplished by means of light weight, high volume solid state drives.
+To address the second, we need both sufficient compute and optimized processing software.
+Finally, ground transfer of final post-processed data products can be accomplished in a variety of ways.
+As we rarely need the full hyper-spectral datacube right away, once can generate the desired data products on board (NDVI for example) and transfer only the relevant information to a ground station
+
 We should now make the argument about the need for improved methods for processing of HSI due the their dramatically larger size, i.e.
@@
 
-In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI  [@robot-team-1].
+In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI together with a  [@robot-team-1].
 In this paper, we present a procedure based on the method of [@muller-georeferencing] for the rapid processing and georeferencing of imagery captured by a pushbroom HSI mounted on an autonomous.

### 2023-09-29 paper/paper.tex
copying markdown from draft.qmd

@@
 
-In this paper, we implement a procedure for rapid georeferencing of hyper-spectral imagery acquired by an autonomous aerial vehicle, and in doing so, demonstrate the feasibility of the platform for real time characterization of novel environments.
+For decades, multi-spectral imagers* have seen wide spread adoption in the remote sensing community as a means to take advantage of the wealth of information contained in the reflectance spectra of materials.
+In addition to the three color filters of traditional cameras, *multi-spectral* imagers, like those deployed on MODIS, Sentinel 2, and other satellite missions, capture many additional features by utilizing wavelength bands ranging from the near-UV, through the visible spectrum, and into the Infrared.
+With this additional information, multi-spectral remote sensing platforms are able to aid in a variety of domains from tracking land change, characterizing deforestation, monitoring erosion, evaluating crop health, and many others (add references here).
 
-In the face of rapidly accelerating global change, there is a demonstrated need for advanced remote sensing technologies. For decades
+(**add a figure showing the different wavelength bands of publically available satellites**)
 
-\subsection{Hyperspectral Imaging}
+These uses are justified by the reflectance features of materials across the electromagnetic spectrum; water has vibrational modes in the IR, pigments have absorption peaks in the visible, etc...(discuss the particular features present in different regions of the reflectance spectrum).
+Many currently used spectral indices like the *normalized difference vegatation index* (NDVI) take advantage of these spectral regions by comparing ratios of pigment sensitive passbands to the constant signals infrared to infer the abundance of chlorophyll, and consequently, the health of plants, to identify forest canopy, etc..(**add citations and expand**)
 
-- multi-spectral and hyper-spectral imaging
-- in remote sensing
-    - discuss satellite remote sensing 
-    - multi-spectral platforms: MODIS, Sentinel, etc... 
-    - upcoming hyper-spectral platforms:
-- from Airplanes
-- Land change tracking (water erosion, deforestation, desertification )
-- Mention popular spectral indices like the NDVI
+However, despite the plethora of successful applications of multi-spectral imaging, more can be accomplished with the additional information provided by fully resolved spectra.
+For example, in the laboratory, spectrophotometry allows the direct determination of the concentrations of chemicals constituents in solution (**add more detail and references**) by deconvolution of a sample spetrum against libraries carefully collected of reference spectra: individual chemicals be uniquely identified by the characterstic location and shape of their absorption features.
+We should mention something about algal blooms-- harmful species display shifted reflectance peaks that can be used to identify toxic species.
+This information is effectively filtered away by the broad passbands of existing (find the spectra used in that book that show the different species of algae).
+To that end, *hyperspectral imagers* (HSI), which sample hundreds of wavelength binds at each pixel, have become the natural next step for remote sensing platforms with many planned to deployed in the coming years (**add references about soon-to-be-deployed HSI satellites**).
 
-\subsection{Georeferencing}
+At the terrestrial level, drones (commonly, quadcoptrs, octocopters, and other similar multi-rotor craft) equipped with cameras are able to utlize techniques of photogrametry together with continuously sampled imagery to produce high quality digital elevation maps, high quality mosaics, 3-dimensional reconstructions, etc...
+These capabilities provide significant aid for structural analysis, smart agriculture, etc...
+Today, kilogram-scale HSI can be comfortably mounted to the payload of film-scale drones such as the AltaX and advancements in spectral sensing such as (**reference Ethan Minot's recent paper**) suggest that sizes of HSI will continue to shrink further expanding their application in this domain.
 
-- Paragraph about the need of georectification 
+The increased spectral resolution of HSI systems poses unique challenges to their adoption for real time applications primarily stemming from the considerable size of generated data files.
+Current data collection workflows see researchers first perform the aerial survey (data collection) and then transfer data to ground based computers for post processing.
+This workflow is well established in the remote sensing community where, as an example, compressed raw imagery from Sentinel-2 are transferred to the ground and then subsequently post processed into their final L1C (top of atmosphere) and L2A (bottom of atmosphere) data products ((**add citation here**)).
+Drone based applications often operate in a similar manner: images or video are collected by a survey and then post-processed and analyzed with software such as Open Drone Map to produce the desired data products (tile mosaics, 3d reconstructions, etc.) (**add citation**).
+For an HSI platform to function in real time, three key computational tasks are critical:
+1. **FileIO**: captured imagery need to be quickly read by the on-board processing computer
+2.
+**Post-processing**: Raw imagery need to be rapidly converted to the chosen data product (typically, Reflectance), and importantly, must be georeferenced so that each image pixel can be located on the ground.
+3. **Ground Transfer**: Sufficient wireless communication must be avaiable to transmit the final
+
+The first can be readily accomplished by means of light weight, high volume solid state drives.
+To address the second, we need both sufficient compute and optimized processing software.
+Finally, ground transfer of final post-processed data products can be accomplished in a variety of ways.
+As we rarely need the full hyper-spectral datacube right away, once can generate the desired data products on board (NDVI for example) and transfer only the relevant information to a ground station
+
+We should now make the argument about the need for improved methods for processing of HSI due the their dramatically larger size, i.e.
+the standard workflow of collecting imagery and then post processing (re: Open Drone Map) is a fantastic and well tested solution but prevents the use in time-critical applications.
+We can also reference the continued improvements to single-board computers such as the raspberry pi 4b (8 Gb of Ram), Jetson family (GPU equipped), and intel nuc (powerful work horses with miniscule form factors).
+To make real-time possible we need two things:
+1. Conversion from raw data (digital counts) to physical units like Reflectance 
+2. Georeferencing of captured imagery so features can be quickly geolocated
+
+We can always re-process the imagery later for an in-depth reanalysis, but for time-critical applications, we need all of the processing to happen on board the drone.
+
+Add a paragraph about georeferencing in particular:
 - Georectification = georeference + orthorectification
 - outline other papers that have discussed georectification techniques:
-        - ground control points 
+    - ground control points  (not reasonable for dangerous or water-based environments)
     - IMU / GPS
@@
 
-\subsection{Drone based Platforms}
+Discuss configurations of imagers and the development of georeferencing strategies, e.g.
+starting with the Muller paper and going to today.
+Mention potential for the incorporation of digital elevation maps together enabled by GPUs and video game engines (**reference that one paper that suggests using Unity or something similar for the projective geometry optimized for Cuda on NVIDIA GPUs**).
 
-- Paragraph about use of drones for remote sensing 
-    - smart agriculture
-    - photogrametry and DEMs (Open Drone Map)
+In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI together with a  \cite{robot-team-1}.
+In this paper, we present a procedure based on the method of \cite{muller-georeferencing} for the rapid processing and georeferencing of imagery captured by a pushbroom HSI mounted on an autonomous.
+Associated code can be freely accessed and downloaded in (**add reference to our repository**)
 
-\subsection{Computational Difficulties}
-
-- Paragraph about difficulties of real time HSI application 
-    - data volume (storage, transfer/streaming)
-    - payload size 
-    - what we really want (usually) isn't the full spectra at each pixel 
-        - spectral indices (NDVI, etc.) 
-        - Chemical concentrations (chlorophyll, crude oil, etc...)
-
-- Paragraph about advances in hyper-spectral imaging technology, drones, and miniaturized computers (e.g. the raspberry pi, jetson nano, intel nuc, etc...)
-
-- Challenges of using HSI in real-time applications: Data volume, processing power, data streaming.
-Data are much to big to be streamed to the ground in real time; for this application, imagery need to be collected, georeferenced, and then turned into data products \emph{onboard the drone} before they can be readily streamed to the ground.
-We can always re-process the imagery later for an in-depth reanalysis, but for time-critical applications, we need all of the processing to happen on board the drone.
-
-- finally, introduce the paper via the Robot team --> e.g. cite the paper and talk about how we're going to focus on the drone in detail in this paper.
+(**This point can be saved for the supervised learning paper**) what we really want (usually) isn't the full spectra at each pixel
 
 IMU - inertial measurement unit
-
-In the realm of remote sensing, the utilization of multi-spectral and hyper-spectral imaging technologies has ushered in a new era of unprecedented capabilities for Earth observation and environmental monitoring.
-Multi-spectral imaging, which captures data across a limited number of discrete spectral bands, and hyper-spectral imaging, which offers a significantly higher number of finely spaced spectral channels, have become invaluable tools for discerning intricate details of our planet's surface and atmosphere.
-These advanced imaging techniques enable researchers to detect and analyze subtle variations in the reflectance, absorption, and emission properties of materials across the electromagnetic spectrum.
-They have found applications in a myriad of fields, from agriculture and forestry to geology and environmental science, by enhancing our ability to discriminate between different land cover types, identify chemical compositions, and monitor changes in vegetation health and atmospheric constituents \cite{remote-sensing-foliage, crop-indices-2000}.
 

### 2023-09-30 1f__extra-plots.jl
added new plot of satellite passbands

@@ -1,0 +1,374 @@
+using CairoMakie
+using MintsMakieRecipes
+using XLSX
+using CSV, DataFrames
+using DataInterpolations
+
+set_theme!(mints_theme)
+update_theme!(
+    figure_padding=30,
+    Axis = (
+        xticklabelsize=20,
+        yticklabelsize=20,
+        xlabelsize=22,
+        ylabelsize=22,
+        titlesize=25,
+    ),
+    Colorbar = (
+        ticklabelsize=20,
+        labelsize=22
+    )
+)
+
+
+
+
+# spectral data from the USGS
+# https://landsat.usgs.gov/spectral-characteristics-viewer
+
+basepath = "./assets/satellite-passbands"
+@assert ispath(basepath)
+
+readdir(basepath)
+
+fnames = [
+    "L8_OLI_RSR.xlsx",
+    "MODIS_PFM_IB_OOB_RSR_merged.xlsx",
+    "S2-SRF_COPE-GSEG-EOPG-TN-15-0007_3.1.xlsx",
+]
+
+files = joinpath.(basepath, fnames)
+
+@assert all(isfile.(files))
+
+
+
+
+
+# --------------------------------------------------------
+# Sentinel 2
+# --------------------------------------------------------
+
+out_name = ["λ", "B1", "B2", "B3", "B4", "B5", "B6", "B7", "B8", "B8A", "B9", "B10", "B11", "B12"]
+
+df_s2a = DataFrame(XLSX.readtable(files[end], "Spectral Responses (S2A)"))
+df_s2b = DataFrame(XLSX.readtable(files[end], "Spectral Responses (S2B)"))
+
+for i ∈ 1:ncol(df_s2a)
+    rename!(df_s2a, i => out_name[i])
+    rename!(df_s2b, i => out_name[i])
+
+    if i == 1
+        df_s2a[!,i] = Int.(df_s2a[!,i])
+        df_s2b[!,i] = Int.(df_s2b[!,i])
+    else
+        df_s2a[!,i] = Float64.(df_s2a[!,i])
+        df_s2b[!,i] = Float64.(df_s2b[!,i])
+    end
+end
+
+
+# --------------------------------------------------------
+# Landsat 8
[…]

### 2023-09-30 paper/paper.tex
Updates from Overleaf

@@
 
-For decades, multi-spectral imagers* have seen wide spread adoption in the remote sensing community as a means to take advantage of the wealth of information contained in the reflectance spectra of materials.
-In addition to the three color filters of traditional cameras, *multi-spectral* imagers, like those deployed on MODIS, Sentinel 2, and other satellite missions, capture many additional features by utilizing wavelength bands ranging from the near-UV, through the visible spectrum, and into the Infrared.
-With this additional information, multi-spectral remote sensing platforms are able to aid in a variety of domains from tracking land change, characterizing deforestation, monitoring erosion, evaluating crop health, and many others (add references here).
+For decades, multi-spectral imagers have seen wide spread adoption in the remote sensing community as a means to take advantage of the wealth of information contained in the reflectance spectra of materials.
+In addition to the three color filters of traditional cameras, multi-spectral imagers, like those deployed on MODIS, Landsat, Sentinel 2, and a plethora of other satellite missions, capture many additional features by utilizing wavelength bands ranging from the near-UV, through the visible spectrum, and into the Infrared.
+With this additional spectral information, multi-spectral remote sensing platforms are able to aid in a variety of domains like vegetation monitoring, land use classification, water quality assessment, smart agriculture, environmental change detection, and disaster management \textbf{(add references)}.
 
-(**add a figure showing the different wavelength bands of publically available satellites**)
+(**add a figure showing the different wavelength bands of publicly available satellites**)
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=12cm]{./assets/passbands.eps}
+    \caption{Components of the Autonomous Drone HSI platform.}
+    \label{fig:drone-components}
+\end{figure}
 
@@
 \section{Materials and Methods}
+
+Make sure to use \textit{nadir-oriented} in description of HSI on the drone.
 

### 2023-09-30 paper/paper.tex
added more figures to paper

@@
 % Full title of the paper (Capitalized)
-\Title{Rapid Georeferencing n of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle}
-
+\Title{Rapid Processing and Georeferencing of Pushbroom Hyperspectral Imagery for Real Time Application by an Autonomous Aerial Vehicle}
+%\Title{A Procedure for the Rapid Processing and Georeferencing of Hyperspectral Imagery for Real-Time use by an Autonomous Aerial Vehicle}
 % MDPI internal command: Title for citation in the left column
@@
 
-(**add a figure showing the different wavelength bands of publicly available satellites**)
 \begin{figure}[H]
     \centering
-    \includegraphics[width=12cm]{./assets/passbands.eps}
-    \caption{Components of the Autonomous Drone HSI platform.}
-    \label{fig:drone-components}
+    \includegraphics[width=15cm]{./assets/passbands.eps}
+    \caption{Relative spectral response for the wavelength passbands of the popular multi-spectral remote sensing sources Sentinel 2A, Sentinel 2B, Landsat 8, and MODIS. Data from the USGS}
+    \label{fig:passbands}
 \end{figure}
@@
 
+\begin{figure}[H]
+    \includegraphics[width=10.5 cm]{./figures/mNDWI_example.png}
+\caption{Sample data product created on-board the aerial vehicle.
+The modified normalized difference water index is computed for each HSI and combined into a map.
+The plume of Rhodamine dye can clearly be seen in the water.\label{fig-map}}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
